### 2023-05-11 paper.tex
first commit

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Ciência e Natura LaTeX Template
% Version 1.0 (19/01/2017)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%----------------------------------------------------------------------------------------
%	DOCUMENT CONFIGURATIONS (not for authors)
%----------------------------------------------------------------------------------------
\documentclass[oneside, a4paper, 12pt]{article}
\usepackage{xcolor}

\usepackage{etoolbox}

\usepackage{ragged2e}

\usepackage{soul}

\usepackage{titling}
\usepackage{fontawesome5}
\usepackage{xifthen}
\usepackage[hidelinks]{hyperref}
%
%----------------------------------------------------------------------------------------
%	TEMPLATE CONFIGURATIONS (not for authors)
%----------------------------------------------------------------------------------------
%
\definecolor{cncolor}{RGB}{0,102,153}
\setul{3pt}{2.5pt}
\setulcolor{cncolor}

\newcommand{\cenSection}[1]{\def\cenSection{\flushleft{\small#1}}}

\newcommand{\englishTitle}[1]{\def\englishTitle{\centering{\large\bf#1}}}
\newcommand{\portugueseTitle}[1]{\def\portugueseTitle{\par{\centering\bf#1}}}

\newcommand{\orcid}[1]{\href{https://orcid.org/#1}{\textcolor[HTML]{A6CE39}{\faOrcid}}}

\newcommand{\authorinfo}[3][]{%
  {\centering\bf
  {\large #2}% author's name
  \ifthenelse{\isempty{#1}}{}% do nothing if ORCID is not provided
    {\hspace{0.1em}\textsuperscript{\footnotesize #3}\hspace{0.1em}{\large\orcid{#1}\hspace{-0.6em}}}
  }
}

\newcommand{\affil}[1]{\def\affil{#1}}
\newcommand{\affiliation}[2]{\textsuperscript{\footnotesize #1}#2\par}

\newcommand{\portugueseAbstract}[1]{\def\portugueseAbstract{
  \flushleft
  {\bf RESUMO}\\[-8pt]
  {\color{cncolor}\rule{50mm}{1.5pt}}
  \par\nobreak\noindent\ignorespaces\justifying#1
}}
%
\newcommand{\englishAbstract}[1]{\def\englishAbstract{
  \flushleft
  {\bf ABSTRACT}\\[-8pt]
  {\color{cncolor}\rule{50mm}{1.5pt}}
  \par\nobreak\noindent\ignorespaces\justifying#1
}}
%
\newcommand{\englishKeywords}[1]{\def\englishKeywords{
\par\smallskip\noindent
  \small{\bf keywords:}~#1
}}
%
\newcommand{\portugueseKeywords}[1]{\def\portugueseKeywords{
\par\smallskip\noindent
  \small{\bf palavras-chave:}~#1
}}
%
%----------------------------------------------------------------------------------------
%	YOUR PACKAGES
%----------------------------------------------------------------------------------------
%
%----------------------------------------------------------------------------------------
%	YOUR NEW COMMANDS
%----------------------------------------------------------------------------------------
%
%----------------------------------------------------------------------------------------
%	PAPER INFO (for authors)
%----------------------------------------------------------------------------------------
%
\cenSection{Chemistry}
%
\englishTitle{The title in English}
%
\portugueseTitle{O título em Português}
%
\author{
  \authorinfo[0000-0002-1825-0097]{Josiah Carberry}{I}, 
  \authorinfo[0000-0002-1825-0097]{Maryln Tall}{II},
  \authorinfo{Dwain Gooslin}{I}
}
%
\affil{ 
  \affiliation{I}{Brown University, USA}
  \affiliation{II}{University of Oxford, UK}
}
%
\portugueseAbstract{
  Mussum Ipsum, cacilds vidis litro abertis. In elementis mé pra quem é amistosis quis leo.Não sou faixa preta cumpadi, 
  sou preto inteiris, inteiris.Tá deprimidis, eu conheço uma cachacis que pode alegrar sua vidis.Quem num gosta di mé, 
  boa gentis num é. Leite de capivaris, leite de mula manquis sem cabeça.Mé faiz elementum girarzis, nisi eros vermeio.
  Detraxit consequat et quo num tendi nada.Casamentiss faiz malandris se pirulitá.
}
%
\portugueseKeywords{aaa, bbb, ccc, ddd}
%
\englishAbstract{
  Mussum Ipsum, cacilds vidis litro abertis. In elementis mé pra quem é amistosis quis leo.Não sou faixa preta cumpadi, 
  sou preto inteiris, inteiris.Tá deprimidis, eu conheço uma cachacis que pode alegrar sua vidis.Quem num gosta di mé, 
  boa gentis num é. Leite de capivaris, leite de mula manquis sem cabeça.Mé faiz elementum girarzis, nisi eros vermeio.
  Detraxit consequat et quo num tendi nada.Casamentiss faiz malandris se pirulitá.
}
%
\englishKeywords{aaa, bbb, ccc, ddd}
%
%----------------------------------------------------------------------------------------
\begin{document}

\cenSection

\englishTitle
\portugueseTitle

\theauthor
\affil

\portugueseAbstract
\portugueseKeywords

\englishAbstract
\englishKeywords

\end{document}

### 2023-05-11 paper.tex
new version

@@
 \usepackage{xcolor}
+\usepackage{tikz}
 
@@
 %
+\newcommand{\issn}[1]{\def\issn{#1}}
+\newcommand{\volume}[1]{\def\volume{#1}}
+\newcommand{\doi}[1]{\def\doi{#1}}
+\newcommand{\issue}[1]{\def\issue{#1}}
+\newcommand{\submitionDate}[1]{\def\submitionDate{#1}}
+\newcommand{\approvalDate}[1]{\def\approvalDate{#1}}
+\newcommand{\publishDate}[1]{\def\publishDate{#1}}
+
+\newcommand{\cncoverheader}{
+  \noindent\begin{tikzpicture}[remember picture, overlay]
+    \begin{scope}[shift={(0,-20mm)}]
+      \node[anchor=south west,inner sep=0mm] at (0, 0) {\includegraphics[height=20mm]{example-image-a}};
+      \node[anchor=south,inner sep=0mm] at (\textwidth/2, 5mm) {\includegraphics[height=10mm]{example-image-b}};
+      \node[anchor=south east, inner sep=0mm] at (\textwidth, 9mm) {\includegraphics[height=12mm]{example-image-c}};
+      \node[left, anchor=east, inner sep = 0mm] at (\textwidth, 6mm) {\footnotesize ISSN \issn};
+      \node[left, anchor=east, inner sep = 0mm] at (\textwidth, 1.5mm) {\bf\footnotesize OPEN~\includegraphics[width=6px]{images/open-access.eps}~ACCESS};
+
+      \draw[line width=1pt, cncolor] (-20mm, -1.5mm) -- (\paperwidth, -1.5mm);
+      \draw node[anchor=north, inner sep=2mm] at (\textwidth / 2, 0) {\footnotesize Ci. e Nat., Santa Maria, v. \volume, \issue, 2022~ • ~\doi};
+      \node[anchor=north, inner sep=2mm, yshift=-4mm] at (\textwidth / 2, 0) {\footnotesize Submissão: \submitionDate~ • ~Aprovação: \approvalDate~ • ~Publicação: \publishDate};
+
+      \draw[line width=1pt, cncolor] (-20mm, -10mm) -- (\paperwidth, -10mm);
+    \end{scope}
+  \end{tikzpicture}
+ \par\vspace{24mm}
+}
+
 \definecolor{cncolor}{RGB}{0,102,153}
@@
 
-\newcommand{\englishTitle}[1]{\def\englishTitle{\centering{\large\bf#1}}}
-\newcommand{\portugueseTitle}[1]{\def\portugueseTitle{\par{\centering\bf#1}}}
+\newcommand{\englishTitle}[1]{\def\englishTitle{\centering{\Large\bf#1\\}}}
+\newcommand{\portugueseTitle}[1]{\def\portugueseTitle{\centering{\large#1}}}
 
@@
 %----------------------------------------------------------------------------------------
+%	PUBLISH INFO (not for authors)
+%----------------------------------------------------------------------------------------
+%
+\issn{2179-460X}
+%
+\volume{44}
+%
+\issue{eXX}
+%
+\doi{https://doi.org/10.5902/2179460Xxxxxx}
+%
+\submitionDate{xx/xx/xx}
+%
+\approvalDate{xx/xx/xx}
+%
+\publishDate{xx/xx/xx}
+%
+%----------------------------------------------------------------------------------------
 %	PAPER INFO (for authors)
@@
 \begin{document}
+\cncoverheader
 

### 2023-05-11 paper.tex
new version

@@
 \documentclass[oneside, a4paper, 12pt]{article}
+
+\usepackage[left=20mm,right=20mm,top=12.5mm,bottom=12mm]{geometry}
+
 \usepackage{xcolor}
@@
       \draw[line width=1pt, cncolor] (-20mm, -1.5mm) -- (\paperwidth, -1.5mm);
-      \draw node[anchor=north, inner sep=2mm] at (\textwidth / 2, 0) {\footnotesize Ci. e Nat., Santa Maria, v. \volume, \issue, 2022~ • ~\doi};
-      \node[anchor=north, inner sep=2mm, yshift=-4mm] at (\textwidth / 2, 0) {\footnotesize Submissão: \submitionDate~ • ~Aprovação: \approvalDate~ • ~Publicação: \publishDate};
+      \draw node[anchor=north, inner sep=2mm] at (\textwidth / 2, 0) {\footnotesize Ci. e Nat., Santa Maria, v. \volume, \issue, 2022~ \textbullet ~~\doi};
+      \node[anchor=north, inner sep=2mm, yshift=-4mm] at (\textwidth / 2, 0) {\footnotesize Submissão: \submitionDate~ \textbullet ~~Aprovação: \approvalDate~ \textbullet ~~Publicação: \publishDate};
 
       \draw[line width=1pt, cncolor] (-20mm, -10mm) -- (\paperwidth, -10mm);
+    \end{scope}
+  \end{tikzpicture}
+ \par\vspace{24mm}
+}
+
+\newcommand{\cncoverfooter}{
+  \noindent\begin{tikzpicture}[remember picture, overlay]
+    \begin{scope}[shift={(0,0)}]
+      \draw[line width=1pt, cncolor] (0, 0) -- (\textwidth, 0);
+      \node[anchor=north west,inner sep=0mm] at (0, -1.5mm) {\includegraphics[height=8mm]{example-image-a}};
+      \node[anchor=west, inner sep=0mm] at (15mm, -5.6mm) {\footnotesize Published by Ciência e Natura under a CC BY-NC-SA 4.0 license.};
     \end{scope}
@@
 
-\newcommand{\affil}[1]{\def\affil{#1}}
+\newcommand{\affil}[1]{\def\affil{\par#1}}
 \newcommand{\affiliation}[2]{\textsuperscript{\footnotesize #1}#2\par}
@@
 \begin{document}
+\thispagestyle{empty}
 \cncoverheader
@@
 \englishKeywords
+\vfill
+\cncoverfooter
 

### 2023-05-11 paper.tex
new version

@@
     \begin{scope}[shift={(0,-20mm)}]
-      \node[anchor=south west,inner sep=0mm] at (0, 0) {\includegraphics[height=20mm]{example-image-a}};
-      \node[anchor=south,inner sep=0mm] at (\textwidth/2, 5mm) {\includegraphics[height=10mm]{example-image-b}};
-      \node[anchor=south east, inner sep=0mm] at (\textwidth, 9mm) {\includegraphics[height=12mm]{example-image-c}};
+      \node[anchor=south west,inner sep=0mm] at (0, 0) {\includegraphics[height=25mm]{images/logo-ufsm.png}};
+      \node[anchor=south,inner sep=0mm] at (\textwidth/2, 7mm) {\includegraphics[height=16mm]{images/logo-ciencia-e-natura.jpg}};
+      \node[anchor=south east, inner sep=0mm] at (\textwidth, 9mm) {\includegraphics[height=17mm]{images/revista.jpg}};
       \node[left, anchor=east, inner sep = 0mm] at (\textwidth, 6mm) {\footnotesize ISSN \issn};
@@
       \draw[line width=1pt, cncolor] (0, 0) -- (\textwidth, 0);
-      \node[anchor=north west,inner sep=0mm] at (0, -1.5mm) {\includegraphics[height=8mm]{example-image-a}};
-      \node[anchor=west, inner sep=0mm] at (15mm, -5.6mm) {\footnotesize Published by Ciência e Natura under a CC BY-NC-SA 4.0 license.};
+      \node[anchor=north west,inner sep=0mm] at (0, -1.5mm) {\includegraphics[height=6.5mm]{images/creativecommons.png}};
+      \node[anchor=west, inner sep=0mm] at (20mm, -5.0mm) {\footnotesize Published by Ciência e Natura under a CC BY-NC-SA 4.0 license.};
     \end{scope}
   \end{tikzpicture}
- \par\vspace{24mm}
+ \par\vspace{10mm}
 }

### 2023-05-13 paper.tex
hummm

@@
 %----------------------------------------------------------------------------------------
-\documentclass[oneside, a4paper, 12pt]{article}
+\documentclass[twoside, a4paper, 12pt]{article}
 
-\usepackage[left=20mm,right=20mm,top=12.5mm,bottom=12mm]{geometry}
+\usepackage[left=20mm,
+            right=20mm,
+            top=12.5mm,
+            bottom=15mm,
+%            headheight=10mm,
+%            footskip=0mm,
+            includehead,
+            includefoot,
+            ]{geometry}
 
@@
 \usepackage[hidelinks]{hyperref}
+
+\usepackage{fancyhdr} % Headers and footers
+
+\usepackage{indentfirst}
 %
@@
 %
+\pagestyle{fancy} % All pages have headers and footers
+\setlength{\headheight}{10mm}
+\setlength{\headsep}{5mm} 
+\setlength{\footskip}{4mm}
+\addtolength{\topmargin}{0mm}
+
+\pagestyle{fancy} % All pages have headers and footers
+\fancyfoot{} % Blank out the default footer
+%header
+\fancyhead[EL]{\thepage~~\textbar{}~\shortHeaderTitle} % 
+\fancyhead[OR]{\shortHeaderAuthors~\textbar{}~~\thepage} % 
+\fancyhead[ER]{} % 
+\fancyhead[OL]{} % 
+%
+\renewcommand\headrule{\vspace{-1mm}\noindent\makebox[\linewidth]{\color{cncolor}\rule{\linewidth}{1.5pt}}}
+%footer
+\fancyfoot[C]{{\color{cncolor}\rule{90mm}{1.5pt}}\\[-3pt]{\footnotesize Ci. e Nat., Santa Maria, v.\volume, \eJournal, {\the\year}}}
+
 \newcommand{\issn}[1]{\def\issn{#1}}
@@
 \newcommand{\doi}[1]{\def\doi{#1}}
-\newcommand{\issue}[1]{\def\issue{#1}}
+\newcommand{\eJournal}[1]{\def\eJournal{#1}}
 \newcommand{\submitionDate}[1]{\def\submitionDate{#1}}
@@
   \noindent\begin{tikzpicture}[remember picture, overlay]
-    \begin{scope}[shift={(0,-20mm)}]
+    \begin{scope}[shift={(0,-10mm)}]
       \node[anchor=south west,inner sep=0mm] at (0, 0) {\includegraphics[height=25mm]{images/logo-ufsm.png}};
@@
       \draw[line width=1pt, cncolor] (-20mm, -1.5mm) -- (\paperwidth, -1.5mm);
-      \draw node[anchor=north, inner sep=2mm] at (\textwidth / 2, 0) {\footnotesize Ci. e Nat., Santa Maria, v. \volume, \issue, 2022~ \textbullet ~~\doi};
+      \draw node[anchor=north, inner sep=2mm] at (\textwidth / 2, 0) {\footnotesize Ci. e Nat., Santa Maria, v. \volume, \eJournal, 2022~ \textbullet ~~\doi};
       \node[anchor=north, inner sep=2mm, yshift=-4mm] at (\textwidth / 2, 0) {\footnotesize Submissão: \submitionDate~ \textbullet ~~Aprovação: \approvalDate~ \textbullet ~~Publicação: \publishDate};
@@
   \end{tikzpicture}
- \par\vspace{24mm}
+ \par\vspace{14mm}
 }
-
+%
 \newcommand{\cncoverfooter}{
@@
   \end{tikzpicture}
- \par\vspace{10mm}
+ \par\vspace{-7mm}
 }
-
+%
 \definecolor{cncolor}{RGB}{0,102,153}
@@
 }}
+
+\newcommand{\shortHeaderTitle}[1]{\def\shortHeaderTitle{#1}}
+\newcommand{\shortHeaderAuthors}[1]{\def\shortHeaderAuthors{#1}}
+
+\makeatletter
+\renewcommand*{\@seccntformat}[1]{\csname the#1\endcsname\hspace{3mm}}
+\makeatother
+
+\setlength{\parskip}{12pt} % 1ex plus 0.5ex minus 0.2ex}
+\setlength{\parindent}{20mm} 
+\setlength{\tabcolsep}{30mm}
+
+\newcommand{\coverpage}{
+  \thispagestyle{empty}
+  \cncoverheader
+
+  \cenSection
+
+  \englishTitle
+  \vspace{5mm}
+  \portugueseTitle
+
+  \theauthor
+  \affil
+
+  \portugueseAbstract
+  \portugueseKeywords
+
+  \englishAbstract
+  \englishKeywords
+  \vfill
+  \cncoverfooter
+  \clearpage
+}
 %
@@
 %
-\issue{eXX}
+\eJournal{eXX}
 %
@@
 }
+
+\shortHeaderTitle{The title}
+\shortHeaderAuthors{Josiiah~{\it~at.~al}}
 %
@@
 \begin{document}
-\thispagestyle{empty}
-\cncoverheader
+  \coverpage
 
-\cenSection
+  Mussum Ipsum, cacilds vidis litro abertis.
+Copo furadis é disculpa de bebadis, arcu quam euismod magna.Nec orci ornare consequat.
+Praesent lacinia ultrices consectetur.
+Sed non ipsum felis.Leite de capivaris, leite de mula manquis sem cabeça.Todo mundo vê os porris que eu tomo, mas ninguém vê os tombis que eu levo!\par
 
-\englishTitle
-\portugueseTitle
+  Admodum accumsan disputationi eu sit.
+Vide electram sadipscing et per.Leite de capivaris, leite de mula manquis sem cabeça.Praesent vel viverra nisi.
+Mauris aliquet nunc non turpis scelerisque, eget.Nullam volutpat risus nec leo commodo, ut interdum diam laoreet.
+Sed non consequat odio.
 
-\theauthor
-\affil
+  Nullam volutpat risus nec leo commodo, ut interdum diam laoreet.
+Sed non consequat odio.Interessantiss quisso pudia ce receita de bolis, mais bolis eu num gostis.Leite de capivaris, leite de mula manquis sem cabeça.Si u mundo tá muito paradis?
+Toma um mé que o mundo vai girarzis!
 
-\portugueseAbstract
-\portugueseKeywords
+  \section{Introduction}
 
-\englishAbstract
-\englishKeywords
-\vfill
-\cncoverfooter
+  Delegadis gente finis, bibendum egestas augue arcu ut est.Casamentiss faiz malandris se pirulitá.Tá deprimidis, eu conheço uma cachacis que pode alegrar sua vidis.Interagi no mé, cursus quis, vehicula ac nisi.
 
+  Praesent vel viverra nisi.
+Mauris aliquet nunc non turpis scelerisque, eget.Admodum accumsan disputationi eu sit.
+Vide electram sadipscing et per.Nec orci ornare consequat.
+Praesent lacinia ultrices consectetur.
+Sed non ipsum felis.Atirei o pau no gatis, per gatis num morreus.
+
+  \subsection{Sub Introduction}
+
+  Pra lá , depois divoltis porris, paradis.A ordem dos tratores não altera o pão duris.Quem num gosta di mé, boa gentis num é.Aenean aliquam molestie leo, vitae iaculis nisl.
+
+  Quem num gosta di mé, boa gentis num é.Sapien in monti palavris qui num significa nadis i pareci latim.Aenean aliquam molestie leo, vitae iaculis nisl.Nec orci ornare consequat.
+Praesent lacinia ultrices consectetur.
+Sed non ipsum felis.
+
+  Cevadis im ampola pa arma uma pindureta.Vehicula non.
+Ut sed ex eros.
+Vivamus sit amet nibh non tellus tristique interdum.Quem num gosta di mé, boa gentis num é.Todo mundo vê os porris que eu tomo, mas ninguém vê os tombis que eu levo!
+
+  Suco de cevadiss deixa as pessoas mais interessantis.Quem num gosta di mim que vai caçá sua turmis!Pra lá , depois divoltis porris, paradis.Não sou faixa preta cumpadi, sou preto inteiris, inteiris.
+
+  Admodum accumsan disputationi eu sit.
+Vide electram sadipscing et per.Atirei o pau no gatis, per gatis num morreus.Quem num gosta di mé, boa gentis num é.Aenean aliquam molestie leo, vitae iaculis nisl.
+
+  Mé faiz elementum girarzis, nisi eros vermeio.Suco de cevadiss deixa as pessoas mais interessantis.Aenean aliquam molestie leo, vitae iaculis nisl.Quem manda na minha terra sou euzis!
+
+  Sapien in monti palavris qui num significa nadis i pareci latim.Quem num gosta di mé, boa gentis num é.Em pé sem cair, deitado sem dormir, sentado sem cochilar e fazendo pose.Mé faiz elementum girarzis, nisi eros vermeio.
+
+  Tá deprimidis, eu conheço uma cachacis que pode alegrar sua vidis.Mé faiz elementum girarzis, nisi eros vermeio.In elementis mé pra quem é amistosis quis leo.Si num tem leite então bota uma pinga aí cumpadi!
+
+  Admodum accumsan disputationi eu sit.
+Vide electram sadipscing et per.Posuere libero varius.
+Nullam a nisl ut ante blandit hendrerit.
+Aenean sit amet nisi.Mé faiz elementum girarzis, nisi eros vermeio.Mais vale um bebadis conhecidiss, que um alcoolatra anonimis.
+
+  Atirei o pau no gatis, per gatis num morreus.A ordem dos tratores não altera o pão duris.Per aumento de cachacis, eu reclamis.Leite de capivaris, leite de mula manquis sem cabeça.
+
+  Quem num gosta di mim que vai caçá sua turmis!Cevadis im ampola pa arma uma pindureta.Tá deprimidis, eu conheço uma cachacis que pode alegrar sua vidis.In elementis mé pra quem é amistosis quis leo.
+
+  Mé faiz elementum girarzis, nisi eros vermeio.Todo mundo vê os porris que eu tomo, mas ninguém vê os tombis que eu levo!Casamentiss faiz malandris se pirulitá.Sapien in monti palavris qui num significa nadis i pareci latim.
+
+  Interagi no mé, cursus quis, vehicula ac nisi.Casamentiss faiz malandris se pirulitá.Quem num gosta di mim que vai caçá sua turmis!Tá deprimidis, eu conheço uma cachacis que pode alegrar sua vidis.
+
+  Quem num gosta di mim que vai caçá sua turmis!Diuretics paradis num copo é motivis de denguis.Quem manda na minha terra sou euzis!Mauris nec dolor in eros commodo tempor.
+Aenean aliquam molestie leo, vitae iaculis nisl.
+
+  Cevadis im ampola pa arma uma pindureta.Interagi no mé, cursus quis, vehicula ac nisi.Todo mundo vê os porris que eu tomo, mas ninguém vê os tombis que eu levo!Paisis, filhis, espiritis santis.
+
+  In elementis mé pra quem é amistosis quis leo.Diuretics paradis num copo é motivis de denguis.Leite de capivaris, leite de mula manquis sem cabeça.Mais vale um bebadis conhecidiss, que um alcoolatra anonimis.
+
+  Delegadis gente finis, bibendum egestas augue arcu ut est.In elementis mé pra quem é amistosis quis leo.Interessantiss quisso pudia ce receita de bolis, mais bolis eu num gostis.Quem num gosta di mim que vai caçá sua turmis!
+
+  Todo mundo vê os porris que eu tomo, mas ninguém vê os tombis que eu levo!Cevadis im ampola pa arma uma pindureta.Casamentiss faiz malandris se pirulitá.Si u mundo tá muito paradis?
+Toma um mé que o mundo vai girarzis!
+
+  Aenean aliquam molestie leo, vitae iaculis nisl.Não sou faixa preta cumpadi, sou preto inteiris, inteiris.Praesent malesuada urna nisi, quis volutpat erat hendrerit non.
+Nam vulputate dapibus.Delegadis gente finis, bibendum egestas augue arcu ut est.
+
+  Diuretics paradis num copo é motivis de denguis.Mauris nec dolor in eros commodo tempor.
+Aenean aliquam molestie leo, vitae iaculis nisl.Si u mundo tá muito paradis?
+Toma um mé que o mundo vai girarzis!Suco de cevadiss, é um leite divinis, qui tem lupuliz, matis, aguis e fermentis.
+
+  Praesent malesuada urna nisi, quis volutpat erat hendrerit non.
+Nam vulputate dapibus.Não sou faixa preta cumpadi, sou preto inteiris, inteiris.Mauris nec dolor in eros commodo tempor.
+Aenean aliquam molestie leo, vitae iaculis nisl.Nec orci ornare consequat.
+Praesent lacinia ultrices consectetur.
+Sed non ipsum felis.
+
+  Si u mundo tá muito paradis?
+Toma um mé que o mundo vai girarzis!Vehicula non.
+Ut sed ex eros.
+Vivamus sit amet nibh non tellus tristique interdum.Suco de cevadiss deixa as pessoas mais interessantis.Paisis, filhis, espiritis santis.
+
+  Aenean aliquam molestie leo, vitae iaculis nisl.Paisis, filhis, espiritis santis.Interessantiss quisso pudia ce receita de bolis, mais bolis eu num gostis.Interagi no mé, cursus quis, vehicula ac nisi.
+
+  Quem num gosta di mim que vai caçá sua turmis!Copo furadis é disculpa de bebadis, arcu quam euismod magna.Interessantiss quisso pudia ce receita de bolis, mais bolis eu num gostis.Leite de capivaris, leite de mula manquis sem cabeça.
+
+  Mauris nec dolor in eros commodo tempor.
+Aenean aliquam molestie leo, vitae iaculis nisl.Paisis, filhis, espiritis santis.Mé faiz elementum girarzis, nisi eros vermeio.Em pé sem cair, deitado sem dormir, sentado sem cochilar e fazendo pose.
+
+  Em pé sem cair, deitado sem dormir, sentado sem cochilar e fazendo pose.Atirei o pau no gatis, per gatis num morreus.Nec orci ornare consequat.
+Praesent lacinia ultrices consectetur.
+Sed non ipsum felis.Per aumento de cachacis, eu reclamis.
+
+  Praesent malesuada urna nisi, quis volutpat erat hendrerit non.
+Nam vulputate dapibus.Quem num gosta di mé, boa gentis num é.Em pé sem cair, deitado sem dormir, sentado sem cochilar e fazendo pose.Viva Forevis aptent taciti sociosqu ad litora torquent.
+
+  Suco de cevadiss, é um leite divinis, qui tem lupuliz, matis, aguis e fermentis.Cevadis im ampola pa arma uma pindureta.Si num tem leite então bota uma pinga aí cumpadi!Quem num gosta di mim que vai caçá sua turmis!
+
+  Si num tem leite então bota uma pinga aí cumpadi!Não sou faixa preta cumpadi, sou preto inteiris, inteiris.Per aumento de cachacis, eu reclamis.Casamentiss faiz malandris se pirulitá.
+
+  Interagi no mé, cursus quis, vehicula ac nisi.Em pé sem cair, deitado sem dormir, sentado sem cochilar e fazendo pose.A ordem dos tratores não altera o pão duris.Suco de cevadiss, é um leite divinis, qui tem lupuliz, matis, aguis e fermentis.
+
+  Atirei o pau no gatis, per gatis num morreus.Interagi no mé, cursus quis, vehicula ac nisi.Interessantiss quisso pudia ce receita de bolis, mais bolis eu num gostis.Praesent vel viverra nisi.
+Mauris aliquet nunc non turpis scelerisque, eget.
+
+  Detraxit consequat et quo num tendi nada.Posuere libero varius.
+Nullam a nisl ut ante blandit hendrerit.
+Aenean sit amet nisi.Diuretics paradis num copo é motivis de denguis.Sapien in monti palavris qui num significa nadis i pareci latim.
+
+  Todo mundo vê os porris que eu tomo, mas ninguém vê os tombis que eu levo!Em pé sem cair, deitado sem dormir, sentado sem cochilar e fazendo pose.Nullam volutpat risus nec leo commodo, ut interdum diam laoreet.
+Sed non consequat odio.Praesent malesuada urna nisi, quis volutpat erat hendrerit non.
+Nam vulputate dapibus.
+
+  Admodum accumsan disputationi eu sit.
+Vide electram sadipscing et per.Todo mundo vê os porris que eu tomo, mas ninguém vê os tombis que eu levo!Mais vale um bebadis conhecidiss, que um alcoolatra anonimis.Cevadis im ampola pa arma uma pindureta.
+
+  Nullam volutpat risus nec leo commodo, ut interdum diam laoreet.
+Sed non consequat odio.Tá deprimidis, eu conheço uma cachacis que pode alegrar sua vidis.Sapien in monti palavris qui num significa nadis i pareci latim.Todo mundo vê os porris que eu tomo, mas ninguém vê os tombis que eu levo!
+
+  Mé faiz elementum girarzis, nisi eros vermeio.Leite de capivaris, leite de mula manquis sem cabeça.Si num tem leite então bota uma pinga aí cumpadi!Casamentiss faiz malandris se pirulitá.
+
+  Si num tem leite então bota uma pinga aí cumpadi!Quem num gosta di mim que vai caçá sua turmis!Pra lá , depois divoltis porris, paradis.Praesent malesuada urna nisi, quis volutpat erat hendrerit non.
+Nam vulputate dapibus.
+
+  Paisis, filhis, espiritis santis.Viva Forevis aptent taciti sociosqu ad litora torquent.Nullam volutpat risus nec leo commodo, ut interdum diam laoreet.
+Sed non consequat odio.Quem manda na minha terra sou euzis!
+
+  Vehicula non.
+Ut sed ex eros.
+Vivamus sit amet nibh non tellus tristique interdum.Cevadis im ampola pa arma uma pindureta.Atirei o pau no gatis, per gatis num morreus.In elementis mé pra quem é amistosis quis leo.
+
+  Interessantiss quisso pudia ce receita de bolis, mais bolis eu num gostis.Praesent malesuada urna nisi, quis volutpat erat hendrerit non.
+Nam vulputate dapibus.A ordem dos tratores não altera o pão duris.Tá deprimidis, eu conheço uma cachacis que pode alegrar sua vidis.
+
+  Cevadis im ampola pa arma uma pindureta.Admodum accumsan disputationi eu sit.
+Vide electram sadipscing et per.Mé faiz elementum girarzis, nisi eros vermeio.Diuretics paradis num copo é motivis de denguis.
+
+  Detraxit consequat et quo num tendi nada.Interagi no mé, cursus quis, vehicula ac nisi.Suco de cevadiss, é um leite divinis, qui tem lupuliz, matis, aguis e fermentis.Vehicula non.
+Ut sed ex eros.
+Vivamus sit amet nibh non tellus tristique interdum.
+
+  In elementis mé pra quem é amistosis quis leo.Sapien in monti palavris qui num significa nadis i pareci latim.Si num tem leite então bota uma pinga aí cumpadi!Nullam volutpat risus nec leo commodo, ut interdum diam laoreet.
+Sed non consequat odio.
+
+  Mais vale um bebadis conhecidiss, que um alcoolatra anonimis.In elementis mé pra quem é amistosis quis leo.Cevadis im ampola pa arma uma pindureta.Per aumento de cachacis, eu reclamis.
+
+  Interessantiss quisso pudia ce receita de bolis, mais bolis eu num gostis.A ordem dos tratores não altera o pão duris.Quem num gosta di mim que vai caçá sua turmis!Nec orci ornare consequat.
+Praesent lacinia ultrices consectetur.
+Sed non ipsum felis.
 \end{document}

### 2023-05-14 paper.tex
new version

@@
             bottom=15mm,
-%            headheight=10mm,
-%            footskip=0mm,
             includehead,
@@
 \usepackage{etoolbox}
-
-\usepackage{ragged2e}
 
@@
 \usepackage{indentfirst}
+
+%\usepackage[natbibapa]{apacite}
+\usepackage[authoryear]{natbib}
 %
@@
 %
+\makeatletter
+\renewcommand*{\@seccntformat}[1]{\csname the#1\endcsname\hspace{3mm}}
+\makeatother
+
 \pagestyle{fancy} % All pages have headers and footers
@@
 \newcommand{\publishDate}[1]{\def\publishDate{#1}}
+\newcommand{\custombullet}{\raisebox{1.3pt}{\tiny\textbullet}}
 
@@
       \node[left, anchor=east, inner sep = 0mm] at (\textwidth, 6mm) {\footnotesize ISSN \issn};
-      \node[left, anchor=east, inner sep = 0mm] at (\textwidth, 1.5mm) {\bf\footnotesize OPEN~\includegraphics[width=6px]{images/open-access.eps}~ACCESS};
+      \node[left, anchor=east, inner sep = 0mm] at (\textwidth, 1.5mm) {\includegraphics[height=4.5mm]{images/acesso-aberto.png}};
 
       \draw[line width=1pt, cncolor] (-20mm, -1.5mm) -- (\paperwidth, -1.5mm);
-      \draw node[anchor=north, inner sep=2mm] at (\textwidth / 2, 0) {\footnotesize Ci. e Nat., Santa Maria, v. \volume, \eJournal, 2022~ \textbullet ~~\doi};
-      \node[anchor=north, inner sep=2mm, yshift=-4mm] at (\textwidth / 2, 0) {\footnotesize Submissão: \submitionDate~ \textbullet ~~Aprovação: \approvalDate~ \textbullet ~~Publicação: \publishDate};
+      \draw node[anchor=north, inner sep=2mm] at (\textwidth / 2, 0) {\footnotesize Ci. e Nat., Santa Maria, v. \volume, \eJournal, 2022 \custombullet~\doi};
+      \node[anchor=north, inner sep=2mm, yshift=-4mm] at (\textwidth / 2, 0) {\footnotesize Submissão: \submitionDate~\custombullet~Aprovação: \approvalDate~\custombullet~Publicação: \publishDate};
 
@@
 
-\makeatletter
-\renewcommand*{\@seccntformat}[1]{\csname the#1\endcsname\hspace{3mm}}
-\makeatother
+\usepackage{ragged2e}
 
-\setlength{\parskip}{12pt} % 1ex plus 0.5ex minus 0.2ex}
-\setlength{\parindent}{20mm} 
-\setlength{\tabcolsep}{30mm}
+\bibliographystyle{apalike}
+%\bibliographystyle{cen}
 
@@
   \clearpage
+
+  \setlength{\parskip}{12pt}
+  \setlength{\parindent}{36pt} 
 }
@@
 Praesent lacinia ultrices consectetur.
-Sed non ipsum felis.
+Sed non ipsum felis.~\citep{Clarke2014, Satulovsky1944}
+
+	\bibliography{references}
+
 \end{document}

### 2023-05-14 paper.tex
new version

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% Ciência e Natura LaTeX Template
-% Version 1.0 (19/01/2017)
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%----------------------------------------------------------------------------------------
-%	DOCUMENT CONFIGURATIONS (not for authors)
-%----------------------------------------------------------------------------------------
-\documentclass[twoside, a4paper, 12pt]{article}
-
-\usepackage[left=20mm,
-            right=20mm,
-            top=12.5mm,
-            bottom=15mm,
-            includehead,
-            includefoot,
-            ]{geometry}
-
-\usepackage{xcolor}
-\usepackage{tikz}
-
-\usepackage{etoolbox}
-
-\usepackage{soul}
-
-\usepackage{titling}
-\usepackage{fontawesome5}
-\usepackage{xifthen}
-\usepackage[hidelinks]{hyperref}
-
-\usepackage{fancyhdr} % Headers and footers
-
-\usepackage{indentfirst}
-
-%\usepackage[natbibapa]{apacite}
-\usepackage[authoryear]{natbib}
-%
-%----------------------------------------------------------------------------------------
-%	TEMPLATE CONFIGURATIONS (not for authors)
-%----------------------------------------------------------------------------------------
-%
-\makeatletter
-\renewcommand*{\@seccntformat}[1]{\csname the#1\endcsname\hspace{3mm}}
-\makeatother
-
-\pagestyle{fancy} % All pages have headers and footers
-\setlength{\headheight}{10mm}
-\setlength{\headsep}{5mm} 
-\setlength{\footskip}{4mm}
-\addtolength{\topmargin}{0mm}
-
-\pagestyle{fancy} % All pages have headers and footers
-\fancyfoot{} % Blank out the default footer
-%header
-\fancyhead[EL]{\thepage~~\textbar{}~\shortHeaderTitle} % 
-\fancyhead[OR]{\shortHeaderAuthors~\textbar{}~~\thepage} % 
-\fancyhead[ER]{} % 
-\fancyhead[OL]{} % 
-%
-\renewcommand\headrule{\vspace{-1mm}\noindent\makebox[\linewidth]{\color{cncolor}\rule{\linewidth}{1.5pt}}}
-%footer
-\fancyfoot[C]{{\color{cncolor}\rule{90mm}{1.5pt}}\\[-3pt]{\footnotesize Ci. e Nat., Santa Maria, v.\volume, \eJournal, {\the\year}}}
-
-\newcommand{\issn}[1]{\def\issn{#1}}
-\newcommand{\volume}[1]{\def\volume{#1}}
-\newcommand{\doi}[1]{\def\doi{#1}}
-\newcommand{\eJournal}[1]{\def\eJournal{#1}}
-\newcommand{\submitionDate}[1]{\def\submitionDate{#1}}
-\newcommand{\approvalDate}[1]{\def\approvalDate{#1}}
-\newcommand{\publishDate}[1]{\def\publishDate{#1}}
-\newcommand{\custombullet}{\raisebox{1.3pt}{\tiny\textbullet}}
-
-\newcommand{\cncoverheader}{
-  \noindent\begin{tikzpicture}[remember picture, overlay]
-    \begin{scope}[shift={(0,-10mm)}]
-      \node[anchor=south west,inner sep=0mm] at (0, 0) {\includegraphics[height=25mm]{images/logo-ufsm.png}};
-      \node[anchor=south,inner sep=0mm] at (\textwidth/2, 7mm) {\includegraphics[height=16mm]{images/logo-ciencia-e-natura.jpg}};
-      \node[anchor=south east, inner sep=0mm] at (\textwidth, 9mm) {\includegraphics[height=17mm]{images/revista.jpg}};
-      \node[left, anchor=east, inner sep = 0mm] at (\textwidth, 6mm) {\footnotesize ISSN \issn};
-      \node[left, anchor=east, inner sep = 0mm] at (\textwidth, 1.5mm) {\includegraphics[height=4.5mm]{images/acesso-aberto.png}};
-
-      \draw[line width=1pt, cncolor] (-20mm, -1.5mm) -- (\paperwidth, -1.5mm);
-      \draw node[anchor=north, inner sep=2mm] at (\textwidth / 2, 0) {\footnotesize Ci. e Nat., Santa Maria, v. \volume, \eJournal, 2022 \custombullet~\doi};
-      \node[anchor=north, inner sep=2mm, yshift=-4mm] at (\textwidth / 2, 0) {\footnotesize Submissão: \submitionDate~\custombullet~Aprovação: \approvalDate~\custombullet~Publicação: \publishDate};
-
-      \draw[line width=1pt, cncolor] (-20mm, -10mm) -- (\paperwidth, -10mm);
-    \end{scope}
-  \end{tikzpicture}
- \par\vspace{14mm}
-}
-%
-\newcommand{\cncoverfooter}{
-  \noindent\begin{tikzpicture}[remember picture, overlay]
-    \begin{scope}[shift={(0,0)}]
-      \draw[line width=1pt, cncolor] (0, 0) -- (\textwidth, 0);
-      \node[anchor=north west,inner sep=0mm] at (0, -1.5mm) {\includegraphics[height=6.5mm]{images/creativecommons.png}};
-      \node[anchor=west, inner sep=0mm] at (20mm, -5.0mm) {\footnotesize Published by Ciência e Natura under a CC BY-NC-SA 4.0 license.};
-    \end{scope}
-  \end{tikzpicture}
- \par\vspace{-7mm}
-}
-%
-\definecolor{cncolor}{RGB}{0,102,153}
-\setul{3pt}{2.5pt}
-\setulcolor{cncolor}
-
-\newcommand{\cenSection}[1]{\def\cenSection{\flushleft{\small#1}}}
-
-\newcommand{\englishTitle}[1]{\def\englishTitle{\centering{\Large\bf#1\\}}}
-\newcommand{\portugueseTitle}[1]{\def\portugueseTitle{\centering{\large#1}}}
-
-\newcommand{\orcid}[1]{\href{https://orcid.org/#1}{\textcolor[HTML]{A6CE39}{\faOrcid}}}
-
-\newcommand{\authorinfo}[3][]{%
-  {\centering\bf
-  {\large #2}% author's name
-  \ifthenelse{\isempty{#1}}{}% do nothing if ORCID is not provided
-    {\hspace{0.1em}\textsuperscript{\footnotesize #3}\hspace{0.1em}{\large\orcid{#1}\hspace{-0.6em}}}
-  }
-}
-
-\newcommand{\affil}[1]{\def\affil{\par#1}}
-\newcommand{\affiliation}[2]{\textsuperscript{\footnotesize #1}#2\par}
-
-\newcommand{\portugueseAbstract}[1]{\def\portugueseAbstract{
-  \flushleft
-  {\bf RESUMO}\\[-8pt]
-  {\color{cncolor}\rule{50mm}{1.5pt}}
-  \par\nobreak\noindent\ignorespaces\justifying#1
-}}
-%
-\newcommand{\englishAbstract}[1]{\def\englishAbstract{
-  \flushleft
-  {\bf ABSTRACT}\\[-8pt]
-  {\color{cncolor}\rule{50mm}{1.5pt}}
-  \par\nobreak\noindent\ignorespaces\justifying#1
-}}
-%
-\newcommand{\englishKeywords}[1]{\def\englishKeywords{
-\par\smallskip\noindent
-  \small{\bf keywords:}~#1
-}}
-%
-\newcommand{\portugueseKeywords}[1]{\def\portugueseKeywords{
-\par\smallskip\noindent
-  \small{\bf palavras-chave:}~#1
-}}
-
-\newcommand{\shortHeaderTitle}[1]{\def\shortHeaderTitle{#1}}
-\newcommand{\shortHeaderAuthors}[1]{\def\shortHeaderAuthors{#1}}
-
-\usepackage{ragged2e}
-
-\bibliographystyle{apalike}
-%\bibliographystyle{cen}
-
-\newcommand{\coverpage}{
-  \thispagestyle{empty}
-  \cncoverheader
-
-  \cenSection
-
-  \englishTitle
-  \vspace{5mm}
-  \portugueseTitle
-
-  \theauthor
-  \affil
-
-  \portugueseAbstract
-  \portugueseKeywords
-
-  \englishAbstract
-  \englishKeywords
-  \vfill
-  \cncoverfooter
-  \clearpage
-
-  \setlength{\parskip}{12pt}
-  \setlength{\parindent}{36pt} 
-}
+\documentclass[english]{cenarticle}
 %
@@
 %
+\yearonfooter{xxxx}
+%
 %----------------------------------------------------------------------------------------
@@
 \shortHeaderTitle{The title}
-\shortHeaderAuthors{Josiiah~{\it~at.~al}}
+\shortHeaderAuthors{Carberry{\it~et~al.}}
 %

### 2023-05-15 authorshipAndContributions.tex
new version

\section*{Author contributions}

1 - Charles Babbage (Corresponding Author)\\
Computer Scientist, Inventor\\
https://orcid.org/1000-0000-0000-0000 \custombullet~charlesbabbage@example.com\\
Contribution: Conceptualization; Methodology; Writing – Original Draft Preparation

2 - Ada Lovelace \\
Mathematician, Writer\\
https://orcid.org/2000-0000-0000-0000 \custombullet~adalovelace@example.com\\
Contribution: Literature Review, Data Analysis, Writing – Review \& Editing

3 - Pierre Curie\\
Physicist\\
https://orcid.org/1111-2222-3333-6666 \custombullet~pierrecurie@example.com\\
Contribution: Methodology, Data Analysis, Writing – Review \& Editing

4 - Marie Curie\\
Physicist, Chemist\\
https://orcid.org/1111-2222-3333-7777 \custombullet~mariecurie@example.com \\
Contribution: Conceptualization, Methodology, Data Analysis, Writing – Review \& Editing

5 - Grace Hopper\\
Computer Scientist\\
https://orcid.org/1111-2222-3333-8888 \custombullet~gracehopper@example.com\\
Contribution: Conceptualization, Methodology, Writing – Original Draft Preparation

6 - Santos Dumont\\
Inventor, Aviator\\
https://orcid.org/1111-2222-3333-9999 \custombullet~santosdumont@example.com\\
Contribution: Conceptualization, Methodology, Writing – Original Draft Preparation

7 - Nikola Tesla\\
Inventor, Electrical Engineer\\
https://orcid.org/1111-2222-3333-0000 \custombullet~nikolatesla@example.com\\
Contribution: Methodology, Data Analysis, Writing – Review \& Editing

8 - Galileu Galilei\\
Physicist, Mathematician\\
https://orcid.org/1111-2222-3333-1111 \custombullet~galileugalilei@example.com\\
Contribution: Conceptualization, Methodology, Writing – Original Draft Preparation

9 - Jane Goodall\\
Primatologist, Anthropologist\\
https://orcid.org/1111-2222-3333-2222 \custombullet~janegoodall@example.com\\
Contribution: Conceptualization, Writing – Original Draft Preparation, Writing – Review \& Editing

10 - Charles Darwin\\
Biologist, Naturalist\\
https://orcid.org/1111-2222-3333-3333 \custombullet~charlesdarwin@example.com\\
Contribution: Literature Review, Writing – Review \& Editing

11 - Barbara McClintock\\
Geneticist\\
https://orcid.org/1111-2222-3333-4444 \custombullet~barbaramcclintock@example.com\\
Contribution: Methodology, Data Analysis, Writing – Original Draft Preparation

### 2023-05-15 paper.tex
new version

@@
 %
+\usepackage{pgfplots}
 %----------------------------------------------------------------------------------------
@@
 %
-\englishTitle{The title in English}
+\englishTitle{Interference of Lightning and Thunder on Radioactivity: A Novel Approach in the air}
 %
@@
 \author{
-  \authorinfo[0000-0002-1825-0097]{Josiah Carberry}{I}, 
-  \authorinfo[0000-0002-1825-0097]{Maryln Tall}{II},
-  \authorinfo{Dwain Gooslin}{I}
+  %\authorinfo[ORCID]{NAME}{AFFILIATION},
+  \authorinfo[0000-0000-0000-0000]{Charles Babbage}{I},
+  \authorinfo[]{Ada Lovelace}{II},
+  \authorinfo[0000-0000-0000-0000]{Pierre Curie}{I},
+  \authorinfo[0000-0000-0000-0000]{Marie Curie}{},
+  \authorinfo[0000-0000-0000-0000]{Grace Hopper}{II},
+  \authorinfo[0000-0000-0000-0000]{Santos Dumont}{},
+  \authorinfo[]{Nikola Tesla}{},
+  \authorinfo[0000-0000-0000-0000]{Galileu Galilei}{I},
+  \authorinfo[0001-0000-0000-0000]{Jane Goodall}{},
+  \authorinfo[0000-0000-0000-0000]{Charles Darwin}{I},
+  \authorinfo[0000-0000-0000-0000]{Barbara McClintock}{}
 }
@@
 \portugueseAbstract{
-  Mussum Ipsum, cacilds vidis litro abertis. In elementis mé pra quem é amistosis quis leo.Não sou faixa preta cumpadi, 
-  sou preto inteiris, inteiris.Tá deprimidis, eu conheço uma cachacis que pode alegrar sua vidis.Quem num gosta di mé, 
-  boa gentis num é. Leite de capivaris, leite de mula manquis sem cabeça.Mé faiz elementum girarzis, nisi eros vermeio.
-  Detraxit consequat et quo num tendi nada.Casamentiss faiz malandris se pirulitá.
+This research paper presents the results of an airborne experiment conducted by a team of multidisciplinary scientists, aimed at studying the interference of lightning and thunder on radioactivity.
+The experiment utilized a specially designed aircraft equipped with sophisticated instrumentation and a computer system for data collection.
+By leveraging the concept of escape velocity, the team was able to gain altitude and enter stormy regions to capture relevant data.
+The study contributes to our understanding of the complex interactions between atmospheric phenomena and radioactivity.
 }
@@
 \englishAbstract{
-  Mussum Ipsum, cacilds vidis litro abertis. In elementis mé pra quem é amistosis quis leo.Não sou faixa preta cumpadi, 
-  sou preto inteiris, inteiris.Tá deprimidis, eu conheço uma cachacis que pode alegrar sua vidis.Quem num gosta di mé, 
-  boa gentis num é. Leite de capivaris, leite de mula manquis sem cabeça.Mé faiz elementum girarzis, nisi eros vermeio.
-  Detraxit consequat et quo num tendi nada.Casamentiss faiz malandris se pirulitá.
+This research paper presents the results of a groundbreaking experiment conducted by a team of multidisciplinary scientists, aimed at studying the interference of lightning and thunder on radioactivity.
+The experiment introduces a unique instrument, the Espiralocirros-nimbodetector, which employs spores of Syagrus romanzoffiana (commonly known as the "coquinhos do mato") to measure air humidity.
+By utilizing this innovative device, the team investigated the complex interactions between lightning, thunder, and radioactivity, providing intriguing insights into this fascinating phenomenon.
 }
 %
-\englishKeywords{aaa, bbb, ccc, ddd}
+\englishKeywords{lightning, thunder, radioactivity, airborne experiment, escape velocity, storm}
 %
@@
 
-  Mussum Ipsum, cacilds vidis litro abertis.
-Copo furadis é disculpa de bebadis, arcu quam euismod magna.Nec orci ornare consequat.
-Praesent lacinia ultrices consectetur.
-Sed non ipsum felis.Leite de capivaris, leite de mula manquis sem cabeça.Todo mundo vê os porris que eu tomo, mas ninguém vê os tombis que eu levo!\par
+\section{Experimental Setup}
+\subsection{The 14 bis Flying Vehicle}
+    To conduct our experiment, we required a specialized flying vehicle capable of navigating stormy weather conditions.
+In this study, we employed the revolutionary 14 bis, an innovative flying vehicle designed specifically for this purpose.
+The 14 bis, a marvel of engineering ingenuity, exhibits exceptional maneuverability and stability, making it the ideal platform for our experiment.\citep{Clarke2014}
 
-  Admodum accumsan disputationi eu sit.
-Vide electram sadipscing et per.Leite de capivaris, leite de mula manquis sem cabeça.Praesent vel viverra nisi.
-Mauris aliquet nunc non turpis scelerisque, eget.Nullam volutpat risus nec leo commodo, ut interdum diam laoreet.
-Sed non consequat odio.
+\section{The Espiralocirros-nimbodetector}
+Mounted securely aboard the 14 bis, the Espiralocirros-nimbodetector, our novel instrument, played a pivotal role in this experiment.
+Designed to measure air humidity using spores of Syagrus romanzoffiana (coquinhos do mato), the Espiralocirros-nimbodetector collected crucial data throughout the flight.
+Its integration with the 14 bis allowed for precise measurements in close proximity to lightning and thunder events, enhancing our understanding of their impact on radioactivity.
 
-  Nullam volutpat risus nec leo commodo, ut interdum diam laoreet.
-Sed non consequat odio.Interessantiss quisso pudia ce receita de bolis, mais bolis eu num gostis.Leite de capivaris, leite de mula manquis sem cabeça.Si u mundo tá muito paradis?
-Toma um mé que o mundo vai girarzis!
+\section{Flight Path and Data Collection}
+The 14 bis, piloted by skilled aviators, embarked on a carefully planned flight path to encounter stormy weather conditions.
+As the vehicle ascended, the Espiralocirros-nimbodetector started collecting air humidity data, capturing valuable information about the atmospheric conditions near lightning and thunder occurrences.
+The 14 bis maneuvered skillfully through turbulent air currents, ensuring accurate and reliable data collection throughout the flight duration.
 
-  \section{Introduction}
+\section{Data Analysis and Results}
+The collected data, comprising air humidity measurements obtained by the Espiralocirros-nimbodetector aboard the 14 bis, underwent comprehensive analysis using advanced statistical techniques.
+By correlating the recorded air humidity levels with lightning and thunder events, we gained insights into the intricate relationships between atmospheric phenomena and radioactivity.
 
-  Delegadis gente finis, bibendum egestas augue arcu ut est.Casamentiss faiz malandris se pirulitá.Tá deprimidis, eu conheço uma cachacis que pode alegrar sua vidis.Interagi no mé, cursus quis, vehicula ac nisi.
+\pgfplotstableread{multiple_functions.dat}{\table}
 
-  Praesent vel viverra nisi.
-Mauris aliquet nunc non turpis scelerisque, eget.Admodum accumsan disputationi eu sit.
-Vide electram sadipscing et per.Nec orci ornare consequat.
-Praesent lacinia ultrices consectetur.
-Sed non ipsum felis.Atirei o pau no gatis, per gatis num morreus.
+\begin{center}
+  \begin{tikzpicture}[scale=0.7][H]
+\begin{axis}[
+    xmin = 0, xmax = 10,
+    ymin = 0, ymax = 1,
+    xtick distance = 1,
+    ytick distance = 0.25,
+    grid = both,
+    minor tick num = 1,
+    major grid style = {lightgray},
+    minor grid style = {lightgray!25},
+    width = \textwidth,
+    height = 0.75\textwidth,
+    legend cell align = {left},
+    legend pos = north west
+]
 
-  \subsection{Sub Introduction}
+\addplot[blue, mark = *] table [x = {x}, y = {y1}] {\table};
 
-  Pra lá , depois divoltis porris, paradis.A ordem dos tratores não altera o pão duris.Quem num gosta di mé, boa gentis num é.Aenean aliquam molestie leo, vitae iaculis nisl.
+\addplot[red, only marks] table [x ={x}, y = {y2}] {\table};
 
-  Quem num gosta di mé, boa gentis num é.Sapien in monti palavris qui num significa nadis i pareci latim.Aenean aliquam molestie leo, vitae iaculis nisl.Nec orci ornare consequat.
-Praesent lacinia ultrices consectetur.
-Sed non ipsum felis.
+\addplot[teal, only marks, mark = x, mark size = 3pt] table [x = {x}, y = {y3}] {\table};
 
-  Cevadis im ampola pa arma uma pindureta.Vehicula non.
-Ut sed ex eros.
-Vivamus sit amet nibh non tellus tristique interdum.Quem num gosta di mé, boa gentis num é.Todo mundo vê os porris que eu tomo, mas ninguém vê os tombis que eu levo!
+\legend{
+    Plot with marks and line, 
+    Plot only with marks,
+    Plot with other type of marks
+}
 
-  Suco de cevadiss deixa as pessoas mais interessantis.Quem num gosta di mim que vai caçá sua turmis!Pra lá , depois divoltis porris, paradis.Não sou faixa preta cumpadi, sou preto inteiris, inteiris.
+\end{axis}
 
-  Admodum accumsan disputationi eu sit.
-Vide electram sadipscing et per.Atirei o pau no gatis, per gatis num morreus.Quem num gosta di mé, boa gentis num é.Aenean aliquam molestie leo, vitae iaculis nisl.
-
-  Mé faiz elementum girarzis, nisi eros vermeio.Suco de cevadiss deixa as pessoas mais interessantis.Aenean aliquam molestie leo, vitae iaculis nisl.Quem manda na minha terra sou euzis!
-
-  Sapien in monti palavris qui num significa nadis i pareci latim.Quem num gosta di mé, boa gentis num é.Em pé sem cair, deitado sem dormir, sentado sem cochilar e fazendo pose.Mé faiz elementum girarzis, nisi eros vermeio.
-
-  Tá deprimidis, eu conheço uma cachacis que pode alegrar sua vidis.Mé faiz elementum girarzis, nisi eros vermeio.In elementis mé pra quem é amistosis quis leo.Si num tem leite então bota uma pinga aí cumpadi!
-
-  Admodum accumsan disputationi eu sit.
-Vide electram sadipscing et per.Posuere libero varius.
-Nullam a nisl ut ante blandit hendrerit.
-Aenean sit amet nisi.Mé faiz elementum girarzis, nisi eros vermeio.Mais vale um bebadis conhecidiss, que um alcoolatra anonimis.
-
-  Atirei o pau no gatis, per gatis num morreus.A ordem dos tratores não altera o pão duris.Per aumento de cachacis, eu reclamis.Leite de capivaris, leite de mula manquis sem cabeça.
-
-  Quem num gosta di mim que vai caçá sua turmis!Cevadis im ampola pa arma uma pindureta.Tá deprimidis, eu conheço uma cachacis que pode alegrar sua vidis.In elementis mé pra quem é amistosis quis leo.
-
-  Mé faiz elementum girarzis, nisi eros vermeio.Todo mundo vê os porris que eu tomo, mas ninguém vê os tombis que eu levo!Casamentiss faiz malandris se pirulitá.Sapien in monti palavris qui num significa nadis i pareci latim.
-
-  Interagi no mé, cursus quis, vehicula ac nisi.Casamentiss faiz malandris se pirulitá.Quem num gosta di mim que vai caçá sua turmis!Tá deprimidis, eu conheço uma cachacis que pode alegrar sua vidis.
-
-  Quem num gosta di mim que vai caçá sua turmis!Diuretics paradis num copo é motivis de denguis.Quem manda na minha terra sou euzis!Mauris nec dolor in eros commodo tempor.
-Aenean aliquam molestie leo, vitae iaculis nisl.
-
-  Cevadis im ampola pa arma uma pindureta.Interagi no mé, cursus quis, vehicula ac nisi.Todo mundo vê os porris que eu tomo, mas ninguém vê os tombis que eu levo!Paisis, filhis, espiritis santis.
-
-  In elementis mé pra quem é amistosis quis leo.Diuretics paradis num copo é motivis de denguis.Leite de capivaris, leite de mula manquis sem cabeça.Mais vale um bebadis conhecidiss, que um alcoolatra anonimis.
-
-  Delegadis gente finis, bibendum egestas augue arcu ut est.In elementis mé pra quem é amistosis quis leo.Interessantiss quisso pudia ce receita de bolis, mais bolis eu num gostis.Quem num gosta di mim que vai caçá sua turmis!
-
-  Todo mundo vê os porris que eu tomo, mas ninguém vê os tombis que eu levo!Cevadis im ampola pa arma uma pindureta.Casamentiss faiz malandris se pirulitá.Si u mundo tá muito paradis?
-Toma um mé que o mundo vai girarzis!
-
-  Aenean aliquam molestie leo, vitae iaculis nisl.Não sou faixa preta cumpadi, sou preto inteiris, inteiris.Praesent malesuada urna nisi, quis volutpat erat hendrerit non.
-Nam vulputate dapibus.Delegadis gente finis, bibendum egestas augue arcu ut est.
-
-  Diuretics paradis num copo é motivis de denguis.Mauris nec dolor in eros commodo tempor.
-Aenean aliquam molestie leo, vitae iaculis nisl.Si u mundo tá muito paradis?
-Toma um mé que o mundo vai girarzis!Suco de cevadiss, é um leite divinis, qui tem lupuliz, matis, aguis e fermentis.
-
-  Praesent malesuada urna nisi, quis volutpat erat hendrerit non.
-Nam vulputate dapibus.Não sou faixa preta cumpadi, sou preto inteiris, inteiris.Mauris nec dolor in eros commodo tempor.
-Aenean aliquam molestie leo, vitae iaculis nisl.Nec orci ornare consequat.
-Praesent lacinia ultrices consectetur.
-Sed non ipsum felis.
-
-  Si u mundo tá muito paradis?
-Toma um mé que o mundo vai girarzis!Vehicula non.
-Ut sed ex eros.
-Vivamus sit amet nibh non tellus tristique interdum.Suco de cevadiss deixa as pessoas mais interessantis.Paisis, filhis, espiritis santis.
-
-  Aenean aliquam molestie leo, vitae iaculis nisl.Paisis, filhis, espiritis santis.Interessantiss quisso pudia ce receita de bolis, mais bolis eu num gostis.Interagi no mé, cursus quis, vehicula ac nisi.
-
-  Quem num gosta di mim que vai caçá sua turmis!Copo furadis é disculpa de bebadis, arcu quam euismod magna.Interessantiss quisso pudia ce receita de bolis, mais bolis eu num gostis.Leite de capivaris, leite de mula manquis sem cabeça.
-
-  Mauris nec dolor in eros commodo tempor.
-Aenean aliquam molestie leo, vitae iaculis nisl.Paisis, filhis, espiritis santis.Mé faiz elementum girarzis, nisi eros vermeio.Em pé sem cair, deitado sem dormir, sentado sem cochilar e fazendo pose.
-
-  Em pé sem cair, deitado sem dormir, sentado sem cochilar e fazendo pose.Atirei o pau no gatis, per gatis num morreus.Nec orci ornare consequat.
-Praesent lacinia ultrices consectetur.
-Sed non ipsum felis.Per aumento de cachacis, eu reclamis.
-
-  Praesent malesuada urna nisi, quis volutpat erat hendrerit non.
-Nam vulputate dapibus.Quem num gosta di mé, boa gentis num é.Em pé sem cair, deitado sem dormir, sentado sem cochilar e fazendo pose.Viva Forevis aptent taciti sociosqu ad litora torquent.
-
-  Suco de cevadiss, é um leite divinis, qui tem lupuliz, matis, aguis e fermentis.Cevadis im ampola pa arma uma pindureta.Si num tem leite então bota uma pinga aí cumpadi!Quem num gosta di mim que vai caçá sua turmis!
-
-  Si num tem leite então bota uma pinga aí cumpadi!Não sou faixa preta cumpadi, sou preto inteiris, inteiris.Per aumento de cachacis, eu reclamis.Casamentiss faiz malandris se pirulitá.
-
-  Interagi no mé, cursus quis, vehicula ac nisi.Em pé sem cair, deitado sem dormir, sentado sem cochilar e fazendo pose.A ordem dos tratores não altera o pão duris.Suco de cevadiss, é um leite divinis, qui tem lupuliz, matis, aguis e fermentis.
-
-  Atirei o pau no gatis, per gatis num morreus.Interagi no mé, cursus quis, vehicula ac nisi.Interessantiss quisso pudia ce receita de bolis, mais bolis eu num gostis.Praesent vel viverra nisi.
-Mauris aliquet nunc non turpis scelerisque, eget.
-
-  Detraxit consequat et quo num tendi nada.Posuere libero varius.
-Nullam a nisl ut ante blandit hendrerit.
-Aenean sit amet nisi.Diuretics paradis num copo é motivis de denguis.Sapien in monti palavris qui num significa nadis i pareci latim.
-
-  Todo mundo vê os porris que eu tomo, mas ninguém vê os tombis que eu levo!Em pé sem cair, deitado sem dormir, sentado sem cochilar e fazendo pose.Nullam volutpat risus nec leo commodo, ut interdum diam laoreet.
-Sed non consequat odio.Praesent malesuada urna nisi, quis volutpat erat hendrerit non.
-Nam vulputate dapibus.
-
-  Admodum accumsan disputationi eu sit.
-Vide electram sadipscing et per.Todo mundo vê os porris que eu tomo, mas ninguém vê os tombis que eu levo!Mais vale um bebadis conhecidiss, que um alcoolatra anonimis.Cevadis im ampola pa arma uma pindureta.
-
-  Nullam volutpat risus nec leo commodo, ut interdum diam laoreet.
-Sed non consequat odio.Tá deprimidis, eu conheço uma cachacis que pode alegrar sua vidis.Sapien in monti palavris qui num significa nadis i pareci latim.Todo mundo vê os porris que eu tomo, mas ninguém vê os tombis que eu levo!
-
-  Mé faiz elementum girarzis, nisi eros vermeio.Leite de capivaris, leite de mula manquis sem cabeça.Si num tem leite então bota uma pinga aí cumpadi!Casamentiss faiz malandris se pirulitá.
-
-  Si num tem leite então bota uma pinga aí cumpadi!Quem num gosta di mim que vai caçá sua turmis!Pra lá , depois divoltis porris, paradis.Praesent malesuada urna nisi, quis volutpat erat hendrerit non.
-Nam vulputate dapibus.
-
-  Paisis, filhis, espiritis santis.Viva Forevis aptent taciti sociosqu ad litora torquent.Nullam volutpat risus nec leo commodo, ut interdum diam laoreet.
-Sed non consequat odio.Quem manda na minha terra sou euzis!
-
-  Vehicula non.
-Ut sed ex eros.
-Vivamus sit amet nibh non tellus tristique interdum.Cevadis im ampola pa arma uma pindureta.Atirei o pau no gatis, per gatis num morreus.In elementis mé pra quem é amistosis quis leo.
-
-  Interessantiss quisso pudia ce receita de bolis, mais bolis eu num gostis.Praesent malesuada urna nisi, quis volutpat erat hendrerit non.
-Nam vulputate dapibus.A ordem dos tratores não altera o pão duris.Tá deprimidis, eu conheço uma cachacis que pode alegrar sua vidis.
-
-  Cevadis im ampola pa arma uma pindureta.Admodum accumsan disputationi eu sit.
-Vide electram sadipscing et per.Mé faiz elementum girarzis, nisi eros vermeio.Diuretics paradis num copo é motivis de denguis.
-
-  Detraxit consequat et quo num tendi nada.Interagi no mé, cursus quis, vehicula ac nisi.Suco de cevadiss, é um leite divinis, qui tem lupuliz, matis, aguis e fermentis.Vehicula non.
-Ut sed ex eros.
-Vivamus sit amet nibh non tellus tristique interdum.
-
-  In elementis mé pra quem é amistosis quis leo.Sapien in monti palavris qui num significa nadis i pareci latim.Si num tem leite então bota uma pinga aí cumpadi!Nullam volutpat risus nec leo commodo, ut interdum diam laoreet.
-Sed non consequat odio.
-
-  Mais vale um bebadis conhecidiss, que um alcoolatra anonimis.In elementis mé pra quem é amistosis quis leo.Cevadis im ampola pa arma uma pindureta.Per aumento de cachacis, eu reclamis.
-
-  Interessantiss quisso pudia ce receita de bolis, mais bolis eu num gostis.A ordem dos tratores não altera o pão duris.Quem num gosta di mim que vai caçá sua turmis!Nec orci ornare consequat.
-Praesent lacinia ultrices consectetur.
-Sed non ipsum felis.~\citep{Clarke2014, Satulovsky1944}
+\end{tikzpicture}
+\end{center}
 
@@
 
+  {\setlength{\parindent}{0pt}
+    \input{authorshipAndContributions.tex}
+  }
+
 \end{document}

### 2023-05-15 authorshipAndContributions.tex
new version

@@
 
-9 - Jane Goodall\\
-Primatologist, Anthropologist\\
-https://orcid.org/1111-2222-3333-2222 \custombullet~janegoodall@example.com\\
-Contribution: Conceptualization, Writing – Original Draft Preparation, Writing – Review \& Editing
-
-10 - Charles Darwin\\
+9 - Charles Darwin\\
 Biologist, Naturalist\\
@@
 
-11 - Barbara McClintock\\
+10 - Barbara McClintock\\
 Geneticist\\

### 2023-05-15 paper.tex
new version

@@
 %
-\portugueseTitle{O título em Português}
+\portugueseTitle{Interferência de Raios e Trovões na Radioatividade: Uma Nova Abordagem no Ar}
 %
@@
   \authorinfo[0000-0000-0000-0000]{Galileu Galilei}{I},
-  \authorinfo[0001-0000-0000-0000]{Jane Goodall}{},
   \authorinfo[0000-0000-0000-0000]{Charles Darwin}{I},
@@
 \portugueseAbstract{
-This research paper presents the results of an airborne experiment conducted by a team of multidisciplinary scientists, aimed at studying the interference of lightning and thunder on radioactivity.
-The experiment utilized a specially designed aircraft equipped with sophisticated instrumentation and a computer system for data collection.
-By leveraging the concept of escape velocity, the team was able to gain altitude and enter stormy regions to capture relevant data.
-The study contributes to our understanding of the complex interactions between atmospheric phenomena and radioactivity.
+Este artigo de pesquisa apresenta os resultados de um experimento conduzido por uma equipe de cientistas multidisciplinares, com o objetivo de estudar a interferência de raios e trovões na radioatividade.
+Ao utilizar o Eletroplumbos-nimbodetector, a equipe investigou as complexas interações entre raios, trovões e radioatividade, proporcionando insights fascinantes sobre esse fenômeno intrigante. 
+A equipe coletou dados precisos e quantitativos sobre a intensidade dos raios, a frequência dos trovões e os níveis de radioatividade durante tempestades.
+Essas informações foram analisadas por meio de algoritmo Foobar, permitindo a identificação de correlações e padrões.
+Além disso, a equipe realizou medições comparativas em áreas livres de atividade elétrica, servindo como um grupo de controle para a comparação dos resultados.
+Essa abordagem meticulosa permitiu uma análise mais precisa dos efeitos específicos da interferência de raios e trovões na radioatividade.
+Os resultados obtidos revelam um aumento significativo nos níveis de radioatividade durante a ocorrência de raios e trovões, indicando uma clara influência desses fenômenos atmosféricos. 
+Essa descoberta desafia as suposições anteriores e contribui para o avanço do conhecimento sobre os efeitos da atividade elétrica na radioatividade. 
+As implicações dessas descobertas são amplas e podem ter aplicações em diversos campos, incluindo a segurança nuclear, a proteção ambiental e até mesmo a previsão de tempestades e seus efeitos potenciais.
 }
 %
-\portugueseKeywords{aaa, bbb, ccc, ddd}
+\portugueseKeywords{raio, trovão, radioatividade, experimento aéreo, velocidade de escape, tempestade}
 %
 \englishAbstract{
-This research paper presents the results of a groundbreaking experiment conducted by a team of multidisciplinary scientists, aimed at studying the interference of lightning and thunder on radioactivity.
-The experiment introduces a unique instrument, the Espiralocirros-nimbodetector, which employs spores of Syagrus romanzoffiana (commonly known as the "coquinhos do mato") to measure air humidity.
-By utilizing this innovative device, the team investigated the complex interactions between lightning, thunder, and radioactivity, providing intriguing insights into this fascinating phenomenon.
+This research paper presents the results of an experiment conducted by a team of multidisciplinary scientists, aimed at studying the interference of lightning and thunder on radioactivity.
+By utilizing the Electroplumbos-nimbodetector, the team investigated the complex interactions between lightning, thunder, and radioactivity, providing fascinating insights into this intriguing phenomenon.
+The team collected accurate and quantitative data on the intensity of lightning, frequency of thunder, and levels of radioactivity during storms.
+This information was analyzed using the Foobar algorithm, allowing for the identification of correlations and patterns.
+Additionally, the team conducted comparative measurements in areas free from electrical activity, serving as a control group for result comparison.
+This meticulous approach enabled a more precise analysis of the specific effects of lightning and thunder interference on radioactivity.
+The obtained results reveal a significant increase in radioactivity levels during the occurrence of lightning and thunder, indicating a clear influence of these atmospheric phenomena. 
+This discovery challenges previous assumptions and contributes to the advancement of knowledge regarding the effects of electrical activity on radioactivity. 
+The implications of these findings are broad and can have applications in various fields, including nuclear safety, environmental protection, and even storm prediction and its potential effects.
 }

### 2023-05-18 paper.tex
new version

@@
 
-\shortHeaderTitle{The title}
-\shortHeaderAuthors{Carberry{\it~et~al.}}
+\shortHeaderTitle{Interference of Lightning and Thunder on Radioactivity: A Novel Approach ...}
+\shortHeaderAuthors{Babbage{\it~et~al.}}
 %
@@
 Este artigo de pesquisa apresenta os resultados de um experimento conduzido por uma equipe de cientistas multidisciplinares, com o objetivo de estudar a interferência de raios e trovões na radioatividade.
-Ao utilizar o Eletroplumbos-nimbodetector, a equipe investigou as complexas interações entre raios, trovões e radioatividade, proporcionando insights fascinantes sobre esse fenômeno intrigante. 
+Ao utilizar o Eletroplumbus-nimbodetector, a equipe investigou as complexas interações entre raios, trovões e radioatividade, proporcionando insights fascinantes sobre esse fenômeno intrigante. 
 A equipe coletou dados precisos e quantitativos sobre a intensidade dos raios, a frequência dos trovões e os níveis de radioatividade durante tempestades.
@@
 This research paper presents the results of an experiment conducted by a team of multidisciplinary scientists, aimed at studying the interference of lightning and thunder on radioactivity.
-By utilizing the Electroplumbos-nimbodetector, the team investigated the complex interactions between lightning, thunder, and radioactivity, providing fascinating insights into this intriguing phenomenon.
+By utilizing the Electroplumbus nimbodetector, the team investigated the complex interactions between lightning, thunder, and radioactivity, providing fascinating insights into this intriguing phenomenon.
 The team collected accurate and quantitative data on the intensity of lightning, frequency of thunder, and levels of radioactivity during storms.
@@
   \coverpage
-
+%
 \section{Experimental Setup}
@@
 In this study, we employed the revolutionary 14 bis, an innovative flying vehicle designed specifically for this purpose.
-The 14 bis, a marvel of engineering ingenuity, exhibits exceptional maneuverability and stability, making it the ideal platform for our experiment.\citep{Clarke2014}
-
-\section{The Espiralocirros-nimbodetector}
-Mounted securely aboard the 14 bis, the Espiralocirros-nimbodetector, our novel instrument, played a pivotal role in this experiment.
-Designed to measure air humidity using spores of Syagrus romanzoffiana (coquinhos do mato), the Espiralocirros-nimbodetector collected crucial data throughout the flight.
+The 14 bis, a marvel of engineering ingenuity, exhibits exceptional maneuverability and stability, making it the ideal platform for our experiment.\citep{Clarke2014}\par
+%
+To conduct our experiment, we required a specialized flying vehicle capable of navigating stormy weather conditions.
+In this study, we employed the revolutionary 14 bis, an innovative flying vehicle designed specifically for this purpose.
+The 14 bis, a marvel of engineering ingenuity, exhibits exceptional maneuverability and stability, making it the ideal platform for our experiment.\citep{Clarke2014}\par
+%
+\section{The Electroplumbus nimbodetector}
+Mounted securely aboard the 14 bis, the Electroplumbos nimbodetector, our novel instrument, played a pivotal role in this experiment.
+Designed to measure air humidity using spores of Syagrus romanzoffiana (coquinhos do mato), the Electroplumbus nimbodetector collected crucial data throughout the flight.
 Its integration with the 14 bis allowed for precise measurements in close proximity to lightning and thunder events, enhancing our understanding of their impact on radioactivity.
-
+%
 \section{Flight Path and Data Collection}
 The 14 bis, piloted by skilled aviators, embarked on a carefully planned flight path to encounter stormy weather conditions.
-As the vehicle ascended, the Espiralocirros-nimbodetector started collecting air humidity data, capturing valuable information about the atmospheric conditions near lightning and thunder occurrences.
+As the vehicle ascended, the Electroplumbus nimbodetector started collecting air humidity data, capturing valuable information about the atmospheric conditions near lightning and thunder occurrences.
 The 14 bis maneuvered skillfully through turbulent air currents, ensuring accurate and reliable data collection throughout the flight duration.
-
+%
 \section{Data Analysis and Results}
-The collected data, comprising air humidity measurements obtained by the Espiralocirros-nimbodetector aboard the 14 bis, underwent comprehensive analysis using advanced statistical techniques.
+The collected data, comprising air humidity measurements obtained by the Electroplumbus nimbodetector aboard the 14 bis, underwent comprehensive analysis using advanced statistical techniques.
 By correlating the recorded air humidity levels with lightning and thunder events, we gained insights into the intricate relationships between atmospheric phenomena and radioactivity.
@@
 \pgfplotstableread{multiple_functions.dat}{\table}
+
+\pgfplotsset{
+  legend style = {font = \large}, % Adjust the font size and style as needed
+  tick label style = {font = \Large}, % Adjust the font size as needed
+  every axis label = {font = \Large}, % Adjust the font size as needed
+}
 
@@
     width = \textwidth,
-    height = 0.75\textwidth,
+    height = 0.6\textwidth,
     legend cell align = {left},
-    legend pos = north west
+    legend pos = north west,
+    tick label style = {font = \scriptsize}, % Adjust the font size as needed
+    every axis label = {font = \small}, % Adjust the font size as needed
+    legend style = {font = \small} % Adjust the font size and style as needed
 ]

### 2023-05-20 paper.tex
new version

@@
 \documentclass[english]{cenarticle}
-%
-%----------------------------------------------------------------------------------------
-%	YOUR PACKAGES
-%----------------------------------------------------------------------------------------
-%
-\usepackage{pgfplots}
-%----------------------------------------------------------------------------------------
-%	YOUR NEW COMMANDS
-%----------------------------------------------------------------------------------------
-%
 %----------------------------------------------------------------------------------------
@@
 %
+%----------------------------------------------------------------------------------------
+%	YOUR PACKAGES
+%----------------------------------------------------------------------------------------
+%
+\usepackage{pgfplots}
+\usepackage{caption}
+\usepackage{graphicx}
+
+\usepackage{amsmath,amsthm,amssymb,amsfonts}
+\usepackage{siunitx}
+
+\usepackage{booktabs}
+\usepackage{multirow}
+%
+%----------------------------------------------------------------------------------------
+%	YOUR CONFIGURATIONS
+%----------------------------------------------------------------------------------------
+%
+\captionsetup{%
+  font=footnotesize,
+  labelfont=bf,
+  singlelinecheck=false,
+  tableposition=top,
+  labelsep=endash,
+  justification=raggedright,
+  margin={0pt,0pt}
+}
+
+\sisetup{math-micro=\text{µ},text-micro=µ}
+%
+%----------------------------------------------------------------------------------------
+%	YOUR NEW COMMANDS
+%----------------------------------------------------------------------------------------
+%
+\renewcommand{\thefigure}{\arabic{figure}}
 %----------------------------------------------------------------------------------------
@@
 Este artigo de pesquisa apresenta os resultados de um experimento conduzido por uma equipe de cientistas multidisciplinares, com o objetivo de estudar a interferência de raios e trovões na radioatividade.
-Ao utilizar o Eletroplumbus-nimbodetector, a equipe investigou as complexas interações entre raios, trovões e radioatividade, proporcionando insights fascinantes sobre esse fenômeno intrigante. 
-A equipe coletou dados precisos e quantitativos sobre a intensidade dos raios, a frequência dos trovões e os níveis de radioatividade durante tempestades.
-Essas informações foram analisadas por meio de algoritmo Foobar, permitindo a identificação de correlações e padrões.
-Além disso, a equipe realizou medições comparativas em áreas livres de atividade elétrica, servindo como um grupo de controle para a comparação dos resultados.
-Essa abordagem meticulosa permitiu uma análise mais precisa dos efeitos específicos da interferência de raios e trovões na radioatividade.
+Utilizando o Electroplumbus nimbodetector, a equipe investigou as complexas interações entre raios, trovões e radioatividade, fornecendo insights fascinantes sobre esse fenômeno intrigante.
+A equipe coletou dados precisos e quantitativos sobre a intensidade dos raios e os níveis de radioatividade durante tempestades.
+Essas informações foram analisadas usando o algoritmo Foobar, permitindo a identificação de correlações e padrões.
+Além disso, a equipe realizou medições comparativas em áreas livres de atividade elétrica, servindo como grupo de controle para comparação de resultados.
+Essa abordagem meticulosa possibilitou uma análise mais precisa dos efeitos específicos da interferência dos raios na radioatividade.
 Os resultados obtidos revelam um aumento significativo nos níveis de radioatividade durante a ocorrência de raios e trovões, indicando uma clara influência desses fenômenos atmosféricos.
-Essa descoberta desafia as suposições anteriores e contribui para o avanço do conhecimento sobre os efeitos da atividade elétrica na radioatividade. 
-As implicações dessas descobertas são amplas e podem ter aplicações em diversos campos, incluindo a segurança nuclear, a proteção ambiental e até mesmo a previsão de tempestades e seus efeitos potenciais.
+Essa descoberta desafia suposições anteriores e contribui para o avanço do conhecimento sobre os efeitos da atividade elétrica na radioatividade.
+As implicações dessas descobertas são amplas e podem ter aplicações em várias áreas, incluindo segurança nuclear, proteção ambiental e até mesmo previsão de tempestades e seus efeitos potenciais.
 }
 %
-\portugueseKeywords{raio, trovão, radioatividade, experimento aéreo, velocidade de escape, tempestade}
+\portugueseKeywords{raio, radioatividade, experimento aéreo, tempestade}
 %
@@
 This research paper presents the results of an experiment conducted by a team of multidisciplinary scientists, aimed at studying the interference of lightning and thunder on radioactivity.
-By utilizing the Electroplumbus nimbodetector, the team investigated the complex interactions between lightning, thunder, and radioactivity, providing fascinating insights into this intriguing phenomenon.
-The team collected accurate and quantitative data on the intensity of lightning, frequency of thunder, and levels of radioactivity during storms.
+By utilizing the Electroplumbus nimbodetector, the team investigated the complex interactions between lightning, and radioactivity, providing fascinating insights into this intriguing phenomenon.
+The team collected accurate and quantitative data on the intensity of lightning, and levels of radioactivity during storms.
 This information was analyzed using the Foobar algorithm, allowing for the identification of correlations and patterns.
 Additionally, the team conducted comparative measurements in areas free from electrical activity, serving as a control group for result comparison.
-This meticulous approach enabled a more precise analysis of the specific effects of lightning and thunder interference on radioactivity.
+This meticulous approach enabled a more precise analysis of the specific effects of lightning interference on radioactivity.
 The obtained results reveal a significant increase in radioactivity levels during the occurrence of lightning and thunder, indicating a clear influence of these atmospheric phenomena.
@@
 %
-\englishKeywords{lightning, thunder, radioactivity, airborne experiment, escape velocity, storm}
+\englishKeywords{lightning, radioactivity, airborne experiment, storm}
 %
@@
 \section{Experimental Setup}
-\subsection{The 14 bis Flying Vehicle}
-To conduct our experiment, we required a specialized flying vehicle capable of navigating stormy weather conditions.
-In this study, we employed the revolutionary 14 bis, an innovative flying vehicle designed specifically for this purpose.
-The 14 bis, a marvel of engineering ingenuity, exhibits exceptional maneuverability and stability, making it the ideal platform for our experiment.\citep{Clarke2014}\par
+\subsection{The 14-Bis flying vehicle}
+The 14-Bis flying vehicle, an innovative experimental apparatus, features an open cockpit design that offers an unobstructed view for the driver during ascents into the skies to collect data within lightning storms.
+The vehicle is equipped with a two clicle kerosene fueled motor \citep{Torrens1992} that drives a large propeller, providing efficient propulsion for navigating through turbulent atmospheric conditions.\par
 %
-To conduct our experiment, we required a specialized flying vehicle capable of navigating stormy weather conditions.
-In this study, we employed the revolutionary 14 bis, an innovative flying vehicle designed specifically for this purpose.
-The 14 bis, a marvel of engineering ingenuity, exhibits exceptional maneuverability and stability, making it the ideal platform for our experiment.\citep{Clarke2014}\par
+Its streamlined shape is optimized for aerodynamic efficiency, minimizing drag and turbulence to facilitate smooth movement through the air.
+The veicle incorporates pairs of rigid horizontal structures projecting from both sides, designed to provide stability and support during flight \citep{Wipo}, enabling the driver to maintain control even in the presence of strong winds and atmospheric disturbances.\par
 %
-\section{The Electroplumbus nimbodetector}
-Mounted securely aboard the 14 bis, the Electroplumbos nimbodetector, our novel instrument, played a pivotal role in this experiment.
-Designed to measure air humidity using spores of Syagrus romanzoffiana (coquinhos do mato), the Electroplumbus nimbodetector collected crucial data throughout the flight.
-Its integration with the 14 bis allowed for precise measurements in close proximity to lightning and thunder events, enhancing our understanding of their impact on radioactivity.
+Within the open cockpit, the driver securely straps into a harness, ready to embark on their mission into lightning storms.
+The propulsion system powered by the kerosene motor generates the necessary thrust for controlled ascent \citep{Torrens1992}, while the open design ensures an immersive experience for the driver, allowing them to observe and collect data in real-time.\par
 %
-\section{Flight Path and Data Collection}
-The 14 bis, piloted by skilled aviators, embarked on a carefully planned flight path to encounter stormy weather conditions.
-As the vehicle ascended, the Electroplumbus nimbodetector started collecting air humidity data, capturing valuable information about the atmospheric conditions near lightning and thunder occurrences.
-The 14 bis maneuvered skillfully through turbulent air currents, ensuring accurate and reliable data collection throughout the flight duration.
+With its purpose-driven design and reliable motor, the 14-Bis flying vehicle represents an instrumental tool for conducting data collection within lightning storms.
+The combination of an open cockpit, sturdy structural elements, and efficient propulsion system allows for precise maneuverability and enables researchers to gather valuable insights into the dynamics of these atmospheric phenomena.
 %
-\section{Data Analysis and Results}
-The collected data, comprising air humidity measurements obtained by the Electroplumbus nimbodetector aboard the 14 bis, underwent comprehensive analysis using advanced statistical techniques.
-By correlating the recorded air humidity levels with lightning and thunder events, we gained insights into the intricate relationships between atmospheric phenomena and radioactivity.
+\begin{figure}[!h]
+  \caption{The 14-bis flying vehicle}
+  \vspace{-3mm} 
+  \begin{center}
+    \includegraphics[width=0.55\textwidth, trim={0 0 0 0},clip]{images/14-bis.jpeg}
+  \end{center}
+  {\footnotesize
+  Source: Biblioteca Digital Gallica, id btv1b8433366m, Public Domain, availiable on \citep{Beau1907}.\\
+  Caption: The 14-bis in its final form, with octagonal-planform interplane ailerons.}
+  \label{fig:triangle2}
+\end{figure}
+
+\subsection{Electroplumbus Nimbodetector}
+
+Within the experimental setup, a key component is the 4th generation Electroplumbus Nimbodetector, a specialized device designed to collect data from sensors and measure radiation during lightning strikes.
+The core device of the Nimbodetector is a modified version of the Plumbus Combobulator, carefully adapted to precisely capture and analyze radiation levels at the exact moment of lightning occurrence.
+
+The Electroplumbus Nimbodetector comprises two sensors strategically positioned on the front and rear of the 14-bis flying vehicle.
+These sensors, with a prism shape, are filled with an enriched Glowing Schleem substance specifically engineered to effectively gather data from lightning discharges.
+The Schleem material exhibits unique properties that enable accurate measurement of radiation within the immediate vicinity of lightning strikes.
+
+To facilitate data transmission, the sensors are connected to the core device of the Electroplumbus Nimbodetector via electrical wires.
+This wired connection ensures reliable and swift data transfer, allowing for further analysis of radiation levels associated with lightning activity.
+
+The inclusion of two sensors in the setup serves a crucial purpose: calculating the distance from the lightning source.
+By analyzing the time difference in data readings between the front and rear sensors, we can accurately estimate the distance traveled by the lightning strike.
+
+\begin{figure}[!h]
+  \newcommand\x{0.25}
+  \caption{The 4th generation of the Electroplumbus Nimbodetector}
+  \begin{center}
+    \vspace{-3mm}
+		\begin{minipage}[t]{\x\linewidth}
+			\includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{images/nimbodetector.png}	
+      \captionsetup{justification=centering, font=footnotesize}
+			\caption*{(a)}\label{fig:triangle2a}
+		\end{minipage}
+		\begin{minipage}[t]{\x\linewidth}
+			\includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{images/sensor.png}	
+      \captionsetup{justification=centering, font=footnotesize}
+			\caption*{(b)}\label{fig:triangle2b}
+		\end{minipage}\\
+  \end{center}%
+  \vspace{-1mm}
+  {\footnotesize
+  Source: Craiyon website, see \citep{Craiyon}.\\
+  Caption: The (a) figure displays the core of the device with the Plumbus Combobulator inside and (b) shows the lightning detector filled by enriched Glowing Schleem substance.\\
+  }
+	\label{fig:triangle2}
+  \end{figure}\vspace{-9mm}
+%
+\subsection{Data Collection}
+
+The data storage component of the Electroplumbus Nimbodetector is an essential element of its operational framework.
+This system employs a carefully engineered adaptation of the Plumbus Combobulator, which offers fault-tolerant characteristics and efficient data preservation.
+
+At the core of the data storage mechanism is the utilization of punched paper, designed to withstand various environmental conditions.
+This robust material ensures the durability and integrity of the captured lightning data, even during adverse weather conditions such as rainfall.
+The waterproof nature of the paper safeguards the data from moisture, allowing for uninterrupted data collection.
+
+The adapted Plumbus Combobulator employs a $\SI{0.47}{\micro\meter}$ needle, precisely marking the punched paper as the lightning data is processed.
+This needle-based mechanism creates a distinct pattern that represents the collected information.
+With each stroke, a tangible record of the lightning data is imprinted onto the punched paper.
+
+The paper-based storage medium enables efficient and reliable data preservation.
+Each $\SI{100}{\milli\meter}$ segment of the punched paper corresponds to a substantial $\SI{1.2E6}{\byte}$ of information.
+This capacity ensures ample storage space for capturing an extensive volume of lightning data during experiments.
+
+\section{Data Analysis}
+
+\subsection{The Branzine}
+
+According to Plumbus Combobulator manufacturer \citep{PlumbusManual}, the Branzine levels can cause Electroplumbus Nimbodetector malfunctions.
+Because that a preliminary exploratory flight was undertaken to examine the influence of altitude on Branzine levels, considering both air samples collected with and without rainfall.
+
+During the flight, air samples were gathered at various altitudes to measure the concentration of Branzine, by using the Branzine detector\footnote{Digital Bz897U, available on $^{\circledR}$Airbone Laboratory Instrument Inc.}.
+The samples were divided into two groups: those collected during rainfall and those obtained under dry conditions.
+This differentiation aimed to explore any potential impact of precipitation on Branzine levels.
+
+The collected data was send to the laboratory, and the results are summarized in the table below:
+
+\begin{table}[!h]
+\caption{Branzine levels}
+\vspace{-6mm}
+\footnotesize
+\begin{center}
+  \begin{tabular}{@{}lccc@{}}
+  \toprule
+                                         & altitude & \multicolumn{2}{c}{Branzine levels {$[ppm]$}} \\ \cmidrule(l){3-4} 
+                                         & {$[m]$}  & on rain             & lack of rain            \\ \midrule
+  \multirow{8}{*}{\rotatebox[origin=c]{90}{under the clouds} } 
+                                         & $100 \pm 1$      & $0.005 \pm 0.001$   &     $0.006 \pm 0.001$  \\
+                                         & $200 \pm 1$      & $1.265 \pm 0.001$   &     $1.260 \pm 0.001$  \\
+                                         & $500 \pm 1$      & $40.1  \pm 0.01$    &      $40.2 \pm 0.01$   \\
+                                         & $1000\pm 1$      & $392   \pm 5$       &      $395  \pm 5$      \\
+                                         & $2000\pm 1$      & $609   \pm 5$       &      $607  \pm 5$      \\
+                                         & $3000\pm 1$      & $2709  \pm 10$      &     $2701  \pm 10$     \\
+                                         & $4000\pm 1$      & $12701 \pm 10$      &     $12699 \pm 10$     \\
+                                         & $5000\pm 1$      & $100831 \pm 10$     &     $100827 \pm 10$    \\ \midrule
+  \multirow{7}{*}{\rotatebox[origin=c]{90}{above the clouds} }
+                                         & $6000\pm 1$       & $-$                &    $280190 \pm 10$                 \\
+                                         & $6200\pm 1$       & $-$                &    $518914 \pm 100$                \\ 
+                                         & $6400\pm 1$       & $-$                &    $819827 \pm 100$                \\ 
+                                         & $6600\pm 1$       & $-$                &    $100827 \pm 100$                \\ 
+                                         & $6800\pm 1$       & $-$                &    $1124225 \pm 1000$              \\ 
+                                         & $7000\pm 1$       & $-$                &    $6131823 \pm 1000$              \\ 
+                                         & $8000\pm 1$       & $-$                &    $9792921 \pm 1000$              \\ \bottomrule
+  \end{tabular}\\[3mm]
+\end{center}
+Caption: The Branzine levels in relation to altitude, over the Atlantic Ocean (August, 1987).\\
+\end{table}
+
+Upon analyzing the data, it was observed that there is a increase in Branzine levels with increasing altitude.
+However, the rise remained below $0.2\%$, indicating an insignificant effect on the Plumbus performance.
+These findings align with prior research \citep{Gagaia1923}, which suggests that Branzine levels typically exhibit a notable increase of over $5\%$ in specific regions such as winter sections or the Bermuda Triangle ($32\%$).
+\vfill
 

### 2023-05-26 paper.tex
new commit

@@
-\documentclass[english]{cenarticle}
+% meia risca meio traço alt+0150
+% heat transfer rate through radiation
+% o core tem termometro do veículo que é separado. A luz aquece o sheeem (baixa capacidade termica) e é determinada a temperatura
+
+\documentclass[portuguese]{cenarticle}
 %----------------------------------------------------------------------------------------
@@
 \usepackage{pgfplots}
-\usepackage{caption}
 \usepackage{graphicx}
@@
 %
-\captionsetup{%
-  font=footnotesize,
-  labelfont=bf,
-  singlelinecheck=false,
-  tableposition=top,
-  labelsep=endash,
-  justification=raggedright,
-  margin={0pt,0pt}
-}
-
 \sisetup{math-micro=\text{µ},text-micro=µ}
@@
 %
-\englishKeywords{lightning, radioactivity, airborne experiment, storm}
+\englishKeywords{Lightning; Radioactivity; Airborne experiment; Storm}
 %
@@
   {\footnotesize
-  Source: Craiyon website, see \citep{Craiyon}.\\
-  Caption: The (a) figure displays the core of the device with the Plumbus Combobulator inside and (b) shows the lightning detector filled by enriched Glowing Schleem substance.\\
+  Source: Craiyon website, see \citep{Craiyon}\\
+  Caption: The (a) figure displays the core of the device with the Plumbus Combobulator inside and (b) shows the lightning detector filled by enriched Glowing Schleem substance\\
   }
@@
 
-At the core of the data storage mechanism is the utilization of punched paper, designed to withstand various environmental conditions.
+At the core of the data storage mechanism is the utilization of punched tape, designed to withstand various environmental conditions.
 This robust material ensures the durability and integrity of the captured lightning data, even during adverse weather conditions such as rainfall.
-The waterproof nature of the paper safeguards the data from moisture, allowing for uninterrupted data collection.
+The waterproof nature of the tape safeguards the data from moisture, allowing for uninterrupted data collection.
 
-The adapted Plumbus Combobulator employs a $\SI{0.47}{\micro\meter}$ needle, precisely marking the punched paper as the lightning data is processed.
+The adapted Plumbus Combobulator employs a $\SI{0.47}{\micro\meter}$ needle, precisely marking the punched tape as the lightning data is processed.
 This needle-based mechanism creates a distinct pattern that represents the collected information.
-With each stroke, a tangible record of the lightning data is imprinted onto the punched paper.
+With each stroke, a tangible record of the lightning data is imprinted onto the punched tape.
 
-The paper-based storage medium enables efficient and reliable data preservation.
-Each $\SI{100}{\milli\meter}$ segment of the punched paper corresponds to a substantial $\SI{1.2E6}{\byte}$ of information.
+The tape-based storage medium enables efficient and reliable data preservation.
+Each $\SI{100}{\milli\meter}$ segment of the punched tape corresponds to a substantial $\SI{1.2E6}{\byte}$ of information.
 This capacity ensures ample storage space for capturing an extensive volume of lightning data during experiments.
@@
 
-\subsection{The Branzine}
+\subsection{The Branzine levels}
 
-According to Plumbus Combobulator manufacturer \citep{PlumbusManual}, the Branzine levels can cause Electroplumbus Nimbodetector malfunctions.
-Because that a preliminary exploratory flight was undertaken to examine the influence of altitude on Branzine levels, considering both air samples collected with and without rainfall.
-
+According to the Plumbus Combobulator manufacturer's manual \citep{PlumbusManual}, high levels of Branzine can potentially lead to malfunctions in the Electroplumbus Nimbodetector.
+Therefore, a preliminary exploratory flight was conducted to investigate the relationship between altitude and Branzine levels.
 During the flight, air samples were gathered at various altitudes to measure the concentration of Branzine, by using the Branzine detector\footnote{Digital Bz897U, available on $^{\circledR}$Airbone Laboratory Instrument Inc.}.
@@
 
-The collected data was send to the laboratory, and the results are summarized in the table below:
+The  data was sent to the laboratory, and the results are bellow summarized:
 
@@
 \caption{Branzine levels}
-\vspace{-6mm}
+\vspace{-5mm}
 \footnotesize
@@
                                          & $200 \pm 1$      & $1.265 \pm 0.001$   &     $1.260 \pm 0.001$  \\
-                                         & $500 \pm 1$      & $40.1  \pm 0.01$    &      $40.2 \pm 0.01$   \\
+                                         & $500 \pm 1$      & $40.1  \pm 0.1$    &      $40.2 \pm 0.1$   \\
                                          & $1000\pm 1$      & $392   \pm 5$       &      $395  \pm 5$      \\
@@
 \end{table}
-
+\vspace{-6mm}
 Upon analyzing the data, it was observed that there is a increase in Branzine levels with increasing altitude.
 However, the rise remained below $0.2\%$, indicating an insignificant effect on the Plumbus performance.
-These findings align with prior research \citep{Gagaia1923}, which suggests that Branzine levels typically exhibit a notable increase of over $5\%$ in specific regions such as winter sections or the Bermuda Triangle ($32\%$).
-\vfill
+These findings align with prior research \citep{Gagaia1923}, which suggests that Branzine levels typically exhibit a notable increase of over $5\%$ in some conditions such as winter seasons or above the Bermuda's Triangle ($32\%$).
+
+\subsection{The radiation levels}
+
+Despite the influence of Branzine on the detector, it has been determined that the Electroplumbus Nimbodetector is safe to use under the tested conditions.
+The Electroplumbus Nimbodetector was successfully installed on the 14-bis flying vehicle, and a series of tests were conducted at altitudes ranging from $\SI{100}{\meter}$ to $\SI{6000}{\meter}$.
+
+The evaluation began by examining the performance of the Nimbus Detector under heavy rain conditions, comparing the recorded data to measurements obtained in a rainless environment above the clouds.
+A total of $\SI{12}{\meter}$ of data were collected and recorded on punched tape, with $\SI{30}{\centi\meter}$ obtained in the absence of rain and the remaining length obtained during rainfall.
+
+After the evaluation, the collected data in the form of punched tape was sent for analysis.
+The punched tape contained the recorded information obtained by the Nimbus Detector during the data collection.
+To process and analyze the data, the Monrobot XI computer was used, employing the Foobar Algorithm programmed in FORTRAN.
+
+\begin{equation}\label{StefanBoltzmannLaw}
+  j^{\star}=\sigma\varepsilon T^{4}
+\end{equation}
+%
+\noindent where,
+%
+\begin{equation}\label{StefanBoltzmannConstant }
+  \sigma=5.6704\times10^{-8} Wm^{-2}K^{-4}
+\end{equation}
+
+\begin{equation}
+  j^{\star}=\sigma\varepsilon T^{4}
+\end{equation}
+
+\begin{equation}\label{StefanBoltzmannLaw}
+  \begin{split}
+    \frac{P}{A}&=j^{\star}=\sigma\varepsilon (T_{v}^{4} - T_{a}^{4}) \\
+  \end{split}
+\end{equation}
+
+\noindent where,
+
+\begin{equation}\label{StefanBoltzmannLaw}
+  \begin{split}
+    P = \frac{Q}{t}
+  \end{split}
+\end{equation}
 
@@
 
+The chart presents the number of lightning strikes detected by the Nimbus Detector within different altitude ranges.
+As altitude increased, the number of recorded lightning strikes also exhibited an upward trend.
+
 \bibliography{references}

### 2023-05-27 paper.tex
new version

@@
 %
-\englishTitle{Interference of Lightning and Thunder on Radioactivity: A Novel Approach in the air}
+\englishTitle{Exploring the Dynamics of Lightning and its Thermal Effects: Insights from Data Collection and Analysis}
 %
-\portugueseTitle{Interferência de Raios e Trovões na Radioatividade: Uma Nova Abordagem no Ar}
+\portugueseTitle{Explorando a Dinâmica dos Raios e seus Efeitos Térmicos: Insights a partir da Coleta e Análise de Dados}
 %
@@
 
-\shortHeaderTitle{Interference of Lightning and Thunder on Radioactivity: A Novel Approach ...}
+\shortHeaderTitle{Exploring the Dynamics of Lightning and its Thermal Effects: Insights from Data ...}
 \shortHeaderAuthors{Babbage{\it~et~al.}}
@@
 \portugueseAbstract{
-Este artigo de pesquisa apresenta os resultados de um experimento conduzido por uma equipe de cientistas multidisciplinares, com o objetivo de estudar a interferência de raios e trovões na radioatividade.
-Utilizando o Electroplumbus nimbodetector, a equipe investigou as complexas interações entre raios, trovões e radioatividade, fornecendo insights fascinantes sobre esse fenômeno intrigante.
-A equipe coletou dados precisos e quantitativos sobre a intensidade dos raios e os níveis de radioatividade durante tempestades.
-Essas informações foram analisadas usando o algoritmo Foobar, permitindo a identificação de correlações e padrões.
-Além disso, a equipe realizou medições comparativas em áreas livres de atividade elétrica, servindo como grupo de controle para comparação de resultados.
-Essa abordagem meticulosa possibilitou uma análise mais precisa dos efeitos específicos da interferência dos raios na radioatividade.
-Os resultados obtidos revelam um aumento significativo nos níveis de radioatividade durante a ocorrência de raios e trovões, indicando uma clara influência desses fenômenos atmosféricos.
-Essa descoberta desafia suposições anteriores e contribui para o avanço do conhecimento sobre os efeitos da atividade elétrica na radioatividade.
-As implicações dessas descobertas são amplas e podem ter aplicações em várias áreas, incluindo segurança nuclear, proteção ambiental e até mesmo previsão de tempestades e seus efeitos potenciais.
+Os relâmpagos, um fenômeno natural poderoso, não só despertam nossa curiosidade, mas também têm um impacto significativo no ambiente circundante.
+Este estudo tem como objetivo investigar a dinâmica dos relâmpagos e seus efeitos térmicos por meio de uma análise abrangente de dados coletados pelo Electroplumbus Nimbodetector, em conjunto com o veículo voador 14-Bis.
+A configuração experimental oferece uma plataforma única para a coleta de dados em tempo real dentro de tempestades de raios, permitindo a exploração dos processos intricados associados às descargas de raios e aos fenômenos térmicos resultantes.
+A correlação entre a intensidade dos raios e a transferência de radiação térmica é examinada por meio de uma série de experimentos de campo e medições.
+Os resultados revelam uma relação significativa, com um aumento na energia transferida por radiação correspondendo a raios de maior intensidade.
+Ao estudar as transições atômicas subjacentes dentro do detector, são obtidos insights sobre a conversão da energia dos relâmpagos em calor no ar circundante.
+Essas descobertas contribuem para nossa compreensão dos fenômenos térmicos induzidos por relâmpagos e lançam as bases para pesquisas adicionais em ciências atmosféricas, meteorologia e estudos ambientais.
+As implicações deste estudo se estendem a medidas de segurança aprimoradas, ciência climática e conhecimento aprofundado da dinâmica atmosférica.
 }
@@
 \englishAbstract{
-This research paper presents the results of an experiment conducted by a team of multidisciplinary scientists, aimed at studying the interference of lightning and thunder on radioactivity.
-By utilizing the Electroplumbus nimbodetector, the team investigated the complex interactions between lightning, and radioactivity, providing fascinating insights into this intriguing phenomenon.
-The team collected accurate and quantitative data on the intensity of lightning, and levels of radioactivity during storms.
-This information was analyzed using the Foobar algorithm, allowing for the identification of correlations and patterns.
-Additionally, the team conducted comparative measurements in areas free from electrical activity, serving as a control group for result comparison.
-This meticulous approach enabled a more precise analysis of the specific effects of lightning interference on radioactivity.
-The obtained results reveal a significant increase in radioactivity levels during the occurrence of lightning and thunder, indicating a clear influence of these atmospheric phenomena.
-This discovery challenges previous assumptions and contributes to the advancement of knowledge regarding the effects of electrical activity on radioactivity.
-The implications of these findings are broad and can have applications in various fields, including nuclear safety, environmental protection, and even storm prediction and its potential effects.
+Lightning, a powerful natural phenomenon, not only captivates our curiosity but also significantly impacts the surrounding environment.
+This study aims to investigate the dynamics of lightning and its thermal effects through a comprehensive analysis of data collected by the Electroplumbus Nimbodetector, in conjunction with the 14-Bis flying vehicle.
+The experimental setup provides a unique platform for real-time data collection within lightning storms, allowing for the exploration of the intricate processes associated with lightning discharges and the resulting thermal phenomena.
+The correlation between the intensity of lightning strikes and the transfer of thermal radiation is examined through a series of field experiments and measurements.
+The results reveal a significant relationship, with an increase in the energy transferred by radiation corresponding to higher intensity lightning strikes.
+By studying the underlying atomic transitions within the detector, insights into the conversion of lightning energy into heat in the surrounding air are gained.
+These findings contribute to our understanding of lightning-induced thermal phenomena and lay the foundation for further research in atmospheric science, meteorology, and environmental studies.
+The implications of this study extend to improved safety measures, climate science, and enhanced knowledge of atmospheric dynamics.
 }
@@
 \begin{document}
+
 \coverpage
+
+\section{Introduction}
+%
+Lightning, a powerful natural phenomenon, has long fascinated scientists and researchers due to its immense energy and unpredictable behavior.
+The study of lightning and its effects on the surrounding environment is crucial for gaining a deeper understanding of atmospheric dynamics and improving safety measures against its potential hazards.
+In particular, the transfer of thermal radiation during lightning strikes plays a significant role in shaping the thermal characteristics of the atmosphere and has far-reaching implications for meteorology, climate science, and environmental studies.\par
+%
+To investigate the dynamics of lightning and its thermal effects, advanced experimental apparatus and specialized devices are required.
+In this paper, we present the results of a comprehensive study conducted using the 14-Bis flying vehicle and the Electroplumbus Nimbodetector, designed specifically for data collection within lightning storms.
+These innovative instruments enable researchers to gather valuable insights into the intricate processes associated with lightning discharges and the resulting thermal phenomena.\par
+%
+In the following sections, we present the experimental setup, data collection methods, and data analysis techniques employed in this study.
+Subsequently, we discuss the results obtained, highlighting the correlation between lightning strikes and the transfer of thermal radiation.
+Finally, we conclude with a summary of the findings, their significance, and future research directions.\par
 %
@@
 
-Within the experimental setup, a key component is the 4th generation Electroplumbus Nimbodetector, a specialized device designed to collect data from sensors and measure radiation during lightning strikes.
-The core device of the Nimbodetector is a modified version of the Plumbus Combobulator, carefully adapted to precisely capture and analyze radiation levels at the exact moment of lightning occurrence.
-
-The Electroplumbus Nimbodetector comprises two sensors strategically positioned on the front and rear of the 14-bis flying vehicle.
-These sensors, with a prism shape, are filled with an enriched Glowing Schleem substance specifically engineered to effectively gather data from lightning discharges.
-The Schleem material exhibits unique properties that enable accurate measurement of radiation within the immediate vicinity of lightning strikes.
-
-To facilitate data transmission, the sensors are connected to the core device of the Electroplumbus Nimbodetector via electrical wires.
-This wired connection ensures reliable and swift data transfer, allowing for further analysis of radiation levels associated with lightning activity.
-
-The inclusion of two sensors in the setup serves a crucial purpose: calculating the distance from the lightning source.
-By analyzing the time difference in data readings between the front and rear sensors, we can accurately estimate the distance traveled by the lightning strike.
-
+  The 4th generation Electroplumbus Nimbodetector is a specialized device designed to collect data from a sensor and measure thermal radiation during lightning strikes.
+The device incorporates a modified version of the Plumbus Combobulator in its core, along with a specially engineered sensor that has a prism shape and is filled with an enriched Glowing Schleem substance.
+The purpose of the device is to gather data on lightning discharges and study their effects on the surrounding air.\par
+  %
+  The sensor within the Electroplumbus Nimbodetector is designed to capture thermal radiation emitted during lightning strikes.
+When a lightning event occurs, the Glowing Schleem inside the prism-shaped sensor heats up.
+Due to the low heat capacity of the Schleem, the temperature rise is rapidly measured, providing instant data on the thermal effects of the lightning discharge.\par
+  %
+  To determine the temperature of the air surrounding the sensor, the Plumbus Combobulator within the device incorporates a conventional thermometer with hight heat capaciity.
+The thermometer is strategically strategically positioned on the rear of the 14-bis flying vehicle to measure the air temperature in the vicinity of the sensor.
+By comparing the temperature of the Schleem-filled sensor and the air temperature measured by the thermometer, we can establish the temperature difference, which is crucial in assessing the impact of the lightning strikes' radiation on the surrounding air.\par
+  %
+  The Electroplumbus Nimbodetector undergoes rigorous calibration and validation processes to ensure accurate and reliable measurements.
+Prior to deployment, the device is calibrated against reference instruments and tested under controlled laboratory conditions to establish its performance characteristics.
+Special attention is given to the sensitivity, precision, and response time of the sensor and thermometer to ensure the accurate capture of data during lightning strikes.
+  %
   \begin{figure}[!h]
@@
     \label{fig:triangle2}
-  \end{figure}\vspace{-9mm}
+    \end{figure}\vspace{-4mm}
   %
@@
 However, the rise remained below $0.2\%$, indicating an insignificant effect on the Plumbus performance.
-These findings align with prior research \citep{Gagaia1923}, which suggests that Branzine levels typically exhibit a notable increase of over $5\%$ in some conditions such as winter seasons or above the Bermuda's Triangle ($32\%$).
+These findings align with prior research \citep{Gagaia1923}, which suggests that Branzine levels typically exhibit a notable increase of over $5\%$ in some conditions such as winter seasons or above the Devil's Triangle ($32\%$).
 
@@
 To process and analyze the data, the Monrobot XI computer was used, employing the Foobar Algorithm programmed in FORTRAN.
+The behavior of the sensor can be described by the Stefan-Boltzmann law, which relates the energy radiated by a black body to its temperature.
+
+According to the Stefan-Boltzmann law, the power radiated by a gray body is proportional to the fourth power of its absolute temperature $T$ and can be expressed as:
 
 \begin{equation}\label{StefanBoltzmannLaw}
-  j^{\star}=\sigma\varepsilon T^{4}
+  j^{\star}=\sigma T^{4}
 \end{equation}
 %
-\noindent where,
+\noindent where $j^{\star}$ represents the black-body radiant emittance, and $\sigma$ is the Stefan-Boltzmann constant ($\sigma=5.6704\times10^{-8} Wm^{-2}K^{-4}$).
 %
-\begin{equation}\label{StefanBoltzmannConstant }
-  \sigma=5.6704\times10^{-8} Wm^{-2}K^{-4}
-\end{equation}
+To calculate the heat transfer rate by radiation (almost entire in the infrared spectrum band), we modify the previous equation by incorporating the emissivity $\varepsilon$ of the sensor, to make the sensor behave like a gray body.
+The modified equation is as follows:
 
 \begin{equation}
-  j^{\star}=\sigma\varepsilon T^{4}
+  \frac{Q}{t}=A\sigma\varepsilon (T_{v}^{4} - T_{a}^{4})
 \end{equation}
+%
+Here, $Q \slash t$ represents the radiationheat transfer rate, taking into account the emissivity of the sensor $\varepsilon$ .
+The emissivity is a dimensionless quantity that varies between $0$ and $1$, where $0$ represents a perfectly reflective surface (no radiation emitted) and $1$ represents a perfectly black body (maximum radiation emitted).
+In this case, the manufacturer's manual establishes the value $\varepsilon = 0.998$.
+Also, $A$ is the surface sensor's area ($A=\SI{128.34}{\milli\meter^2}$).
 
-\begin{equation}\label{StefanBoltzmannLaw}
-  \begin{split}
-    \frac{P}{A}&=j^{\star}=\sigma\varepsilon (T_{v}^{4} - T_{a}^{4}) \\
-  \end{split}
-\end{equation}
+\section{Results}
 
-\noindent where,
-
-\begin{equation}\label{StefanBoltzmannLaw}
-  \begin{split}
-    P = \frac{Q}{t}
-  \end{split}
-\end{equation}
+The analysis of data collected by the Electroplumbus Nimbodetector reveals a significant correlation between the intensity of lightning strikes and the transfer of thermal radiation.
+Through a series of field experiments and measurements, we observed a consistent increase in the energy transferred by radiation during lightning events.
 
@@
 
+The chart presented in Figure 1 illustrates the relationship between the intensity of lightning strikes and the corresponding heat transfer rate by radiation.
+As the intensity of the lightning strike increases, there is a clear upward trend in the energy transferred.
+This observation supports the hypothesis that lightning strikes contribute to an enhanced transfer of thermal radiation to the surrounding air.
+
+The strong correlation observed between lightning strikes and the energy transferred by radiation reinforces the reliability of the data collected by the Electroplumbus Nimbodetector.
+These findings provide valuable insights into the thermal dynamics associated with lightning discharges and contribute to a better understanding of the effects of lightning on the surrounding environment.
+
+Moreover, it is important to note that light alone cannot directly heat gas molecules.
+Instead, during a lightning strike, the light emitted excites the electrons in atoms within the detector.
+These atoms are already vibrating at a certain frequency.
+Some of these atoms vibrate with sufficient vigor that their vibrational energy matches the electronic energy (photons) absorbed from the lightning, effectively reaching resonance with the solar energy.
+As a result, these atoms undergo a quantum transition from being "electronically excited" to "vibrationally excited," causing the entire atom to move.
+The surrounding air perceives this excited vibration as "heat."
+
+This mechanism provides a deeper understanding of how the energy from a lightning strike is converted into thermal energy in the air.
+By studying the vibrational and electronic transitions occurring within the atoms of the detector, we can further elucidate the intricate processes involved in the thermal effects of lightning discharges.
+
+In conclusion, this study demonstrates a strong correlation between the intensity of lightning strikes and the transfer of thermal radiation.
+The data collected by the Electroplumbus Nimbodetector, along with the presented chart, provides robust evidence supporting this relationship.
+Additionally, the exploration of the underlying processes involving electronic and vibrational transitions within the detector atoms enhances our comprehension of how lightning energy is converted into heat in the surrounding air.
+These findings contribute to the scientific understanding of lightning-induced thermal phenomena and lay the foundation for future research in this field.
+
 \bibliography{references}

### 2023-05-27 paper.tex
new version

@@
-% meia risca meio traço alt+0150
-% heat transfer rate through radiation
-% o core tem termometro do veículo que é separado. A luz aquece o sheeem (baixa capacidade termica) e é determinada a temperatura
-
-\documentclass[portuguese]{cenarticle}
+\documentclass[english]{cenarticle}
 %----------------------------------------------------------------------------------------
@@
 \usepackage{multirow}
+
+\usepackage{listings}
 %
@@
 %
+\lstset{language=Fortran,
+    basicstyle=\footnotesize\ttfamily,
+    keywordstyle=\color{blue}\bfseries,
+    commentstyle=\itshape,
+    stringstyle=\itshape\color{magenta},
+    numbers=left,
+    numberstyle=\color{gray}\footnotesize\ttfamily,
+    numbersep=9pt,
+    showspaces=false,
+    showstringspaces=false,
+    breaklines=true,
+    tabsize=4,
+    frame=leftline,
+    framerule=1pt,
+    rulecolor=\color{cncolor},
+    morekeywords={program, end, subroutine, end subroutine, if, then, else, endif, do, enddo, real, integer, logical, dimension, allocatable, intent, call}
+}
+%
 %----------------------------------------------------------------------------------------
@@
 %
-\renewcommand{\thefigure}{\arabic{figure}}
+\newcommand{\citeauthoryearpage}[2]{
+  (\citeauthor{#1}, \citeyear{#1}, p. #2)
+}
+%
+\newcommand{\citeapud}[3]{
+  (\citeauthor{#1} {\it apud} \citeauthor{#2}, \citeyear{#2}, p. #3)
+}
+
 %----------------------------------------------------------------------------------------
@@
   \authorinfo[0000-0000-0000-0000]{Charles Babbage}{I},
-  \authorinfo[]{Ada Lovelace}{II},
+  \authorinfo[]{Ada Lovelace}{I},
   \authorinfo[0000-0000-0000-0000]{Pierre Curie}{I},
   \authorinfo[0000-0000-0000-0000]{Marie Curie}{},
-  \authorinfo[0000-0000-0000-0000]{Grace Hopper}{II},
-  \authorinfo[0000-0000-0000-0000]{Santos Dumont}{},
+  \authorinfo[0000-0000-0000-0000]{Grace Hopper}{I},
+  \authorinfo[0000-0000-0000-0000]{Santos Dumont}{II},
   \authorinfo[]{Nikola Tesla}{},
@@
 \affil{ 
-  \affiliation{I}{Brown University, USA}
-  \affiliation{II}{University of Oxford, UK}
+  \affiliation{I}{Laboratory 84, Kensal Green University, No 23003, Harrow Road, Queens Park, London, UK}
+  \affiliation{II}{Botafogo Departament, São João Batista University, Rio de Janeiro City, RJ, Brazil}
 }
@@
 %
-\portugueseKeywords{raio, radioatividade, experimento aéreo, tempestade}
+\portugueseKeywords{Raio; Radiação; Experimento Aéreo; Tempestade}
 %
@@
 %
-\englishKeywords{Lightning; Radioactivity; Airborne experiment; Storm}
+\englishKeywords{Lightning; Radiation; Airborne experiment; Storm}
 %
@@
 %
+\longquotation{Two difficulties are encountered in studying radiation within absorbing, emitting, and scattering media that make these studies, to say the least, challenging.
+First, absorption and emission of energy are occurring not only at system boundaries, but at every local point within the medium [...].
+A second difficulty is that spectral effects are often much more pronounced in gases than for solid surfaces.
+\citeauthoryearpage{Siegel1968}{2}}
+%
 To investigate the dynamics of lightning and its thermal effects, advanced experimental apparatus and specialized devices are required.
@@
 The 14-Bis flying vehicle, an innovative experimental apparatus, features an open cockpit design that offers an unobstructed view for the driver during ascents into the skies to collect data within lightning storms.
-The vehicle is equipped with a two clicle kerosene fueled motor \citep{Torrens1992} that drives a large propeller, providing efficient propulsion for navigating through turbulent atmospheric conditions.\par
+The vehicle is equipped with a two clicle kerosene fueled motor \citep{Torrens1992} that drives a large propeller, providing efficient propulsion for navigating through turbulent atmospheric conditions \citeapud{Pimenta1987}{Torrens1992}{46}.
+%
+\begin{figure}[!h]
+  \caption{The 14-bis flying vehicle}
+  \vspace{-3mm} 
+  \begin{center}
+    \includegraphics[width=0.55\textwidth, trim={0 0 0 0},clip]{images/14-bis.jpeg}
+  \end{center}
+  {\footnotesize
+  Source: Biblioteca Digital Gallica, id btv1b8433366m, Public Domain, availiable on \citep{Beau1907}\\
+  Caption: The 14-bis in its final form, with octagonal-planform interplane ailerons}
+    \label{fig:triangle2}
+\end{figure}
 %
@@
 %
-\begin{figure}[!h]
-  \caption{The 14-bis flying vehicle}
-  \vspace{-3mm} 
-  \begin{center}
-    \includegraphics[width=0.55\textwidth, trim={0 0 0 0},clip]{images/14-bis.jpeg}
-  \end{center}
-  {\footnotesize
-  Source: Biblioteca Digital Gallica, id btv1b8433366m, Public Domain, availiable on \citep{Beau1907}.\\
-  Caption: The 14-bis in its final form, with octagonal-planform interplane ailerons.}
-    \label{fig:triangle2}
-  \end{figure}
-
   \subsection{Electroplumbus Nimbodetector}
@@
     \label{fig:triangle2}
-    \end{figure}\vspace{-4mm}
+    \end{figure}\vspace{-10mm}
   %
@@
 
-\section{Results}
+\section{Results and Discussion}
 
@@
 The chart presents the number of lightning strikes detected by the Nimbus Detector within different altitude ranges.
-As altitude increased, the number of recorded lightning strikes also exhibited an upward trend.
-
+As altitude increased, the number of recorded lightning strikes also exhibited an upward trend.\par
+%
 The chart presented in Figure 1 illustrates the relationship between the intensity of lightning strikes and the corresponding heat transfer rate by radiation.
 As the intensity of the lightning strike increases, there is a clear upward trend in the energy transferred.
-This observation supports the hypothesis that lightning strikes contribute to an enhanced transfer of thermal radiation to the surrounding air.
-
+This observation supports the hypothesis that lightning strikes contribute to an enhanced transfer of thermal radiation to the surrounding air.\par
+%
 The strong correlation observed between lightning strikes and the energy transferred by radiation reinforces the reliability of the data collected by the Electroplumbus Nimbodetector.
-These findings provide valuable insights into the thermal dynamics associated with lightning discharges and contribute to a better understanding of the effects of lightning on the surrounding environment.
-
+These findings provide valuable insights into the thermal dynamics associated with lightning discharges and contribute to a better understanding of the effects of lightning on the surrounding environment.\par
+%
 Moreover, it is important to note that light alone cannot directly heat gas molecules.
@@
 As a result, these atoms undergo a quantum transition from being "electronically excited" to "vibrationally excited," causing the entire atom to move.
-The surrounding air perceives this excited vibration as "heat."
-
+The surrounding air perceives this excited vibration as "heat."\par
+%
 This mechanism provides a deeper understanding of how the energy from a lightning strike is converted into thermal energy in the air.
-By studying the vibrational and electronic transitions occurring within the atoms of the detector, we can further elucidate the intricate processes involved in the thermal effects of lightning discharges.
-
+By studying the vibrational and electronic transitions occurring within the atoms of the detector, we can further elucidate the intricate processes involved in the thermal effects of lightning discharges.\par
+%
 In conclusion, this study demonstrates a strong correlation between the intensity of lightning strikes and the transfer of thermal radiation.
@@
 
+\section*{Acknowledgements}
+
+We gratefully acknowledge the Lupus Institute for their financial support, which has made this work possible.
+Also, we want to express our sincere appreciation to the open.ai for its invaluable assistance in the development of this fictional scientific paper.
+
 \bibliography{references}
 
-  {\setlength{\parindent}{0pt}
-    \input{authorshipAndContributions.tex}
-  }
+\theauthorcontributions
+
+\howtocite
+
+\section*{Appendix}
+\lstinputlisting[caption=Foobar program, label={lst:listing-f90}, language=Fortran]{foobar.f90}
 

### 2023-05-27 foobar.f90

@@ -1,0 +1,25 @@
+PROGRAM FOOBAR
+  IMPLICIT NONE
+
+  INTEGER :: N, I
+  CHARACTER(LEN=9) :: MESSAGE
+
+  WRITE(*, *) 'Enter a positive integer:'
+  READ(*, *) N
+
+  DO I = 1, N
+     IF (MOD(I, 3) == 0 .AND. MOD(I, 5) == 0) THEN
+        MESSAGE = 'FOOBAR'
+     ELSEIF (MOD(I, 3) == 0) THEN
+        MESSAGE = 'FOO'
+     ELSEIF (MOD(I, 5) == 0) THEN
+        MESSAGE = 'BAR'
+     ELSE
+        WRITE(*, *) I
+        CONTINUE
+     ENDIF
+
+     WRITE(*, *) MESSAGE
+  END DO
+
+END PROGRAM FOOBAR

### 2023-05-31 paper.tex
new version

@@
 \documentclass[english]{cenarticle}
+%
 %----------------------------------------------------------------------------------------
@@
 \usepackage{graphicx}
-
+%
 \usepackage{amsmath,amsthm,amssymb,amsfonts}
 \usepackage{siunitx}
-
+%
 \usepackage{booktabs}
 \usepackage{multirow}
-
+%
 \usepackage{listings}
+%
+\usepackage{draftwatermark}
 %
@@
     rulecolor=\color{cncolor},
+    firstnumber=1,
     morekeywords={program, end, subroutine, end subroutine, if, then, else, endif, do, enddo, real, integer, logical, dimension, allocatable, intent, call}
 }
+%
+\SetWatermarkText{[Fake]}
+\SetWatermarkScale{0.8}
 %
@@
 }
-
+%
 %----------------------------------------------------------------------------------------
@@
 }
-
+%
 \shortHeaderTitle{Exploring the Dynamics of Lightning and its Thermal Effects: Insights from Data ...}
@@
 \begin{document}
-
+%
 \coverpage
-
+%
 \section{Introduction}
@@
 %
+To investigate the dynamics of lightning and its thermal effects, advanced experimental apparatus and specialized devices are required.
+In this paper, we present the results of a comprehensive study conducted using the 14-Bis flying (figure \ref{fig:flying_veicle}) vehicle and the Electroplumbus Nimbodetector (figure \ref{fig:electroplumbus}), designed specifically for data collection within lightning storms.
+These innovative instruments enable researchers to gather valuable insights into the intricate processes associated with lightning discharges and the resulting thermal phenomena.\par
+%
 \longquotation{Two difficulties are encountered in studying radiation within absorbing, emitting, and scattering media that make these studies, to say the least, challenging.
@@
 \citeauthoryearpage{Siegel1968}{2}}
-%
-To investigate the dynamics of lightning and its thermal effects, advanced experimental apparatus and specialized devices are required.
-In this paper, we present the results of a comprehensive study conducted using the 14-Bis flying vehicle and the Electroplumbus Nimbodetector, designed specifically for data collection within lightning storms.
-These innovative instruments enable researchers to gather valuable insights into the intricate processes associated with lightning discharges and the resulting thermal phenomena.\par
 %
@@
   Caption: The 14-bis in its final form, with octagonal-planform interplane ailerons}
-    \label{fig:triangle2}
+    \label{fig:flying_veicle}
 \end{figure}
@@
   \subsection{Electroplumbus Nimbodetector}
-
-  The 4th generation Electroplumbus Nimbodetector is a specialized device designed to collect data from a sensor and measure thermal radiation during lightning strikes.
-The device incorporates a modified version of the Plumbus Combobulator in its core, along with a specially engineered sensor that has a prism shape and is filled with an enriched Glowing Schleem substance.
+%
+  The 4th generation Electroplumbus Nimbodetector (figure \ref{fig:electroplumbus}) is a specialized device designed to collect data from a sensor and measure thermal radiation during lightning strikes.
+The device incorporates a modified version of the Plumbus Combobulator in its core (figure \ref{fig:electroplumbus}a) , along with a specially engineered sensor (figure \ref{fig:electroplumbus}b) that has a prism shape and is filled with an enriched Glowing Schleem substance.
 The purpose of the device is to gather data on lightning discharges and study their effects on the surrounding air.\par
@@
   }
-    \label{fig:triangle2}
+  \label{fig:electroplumbus}
   \end{figure}\vspace{-10mm}
@@
 \subsection{Data Collection}
-
+%
 The data storage component of the Electroplumbus Nimbodetector is an essential element of its operational framework.
-This system employs a carefully engineered adaptation of the Plumbus Combobulator, which offers fault-tolerant characteristics and efficient data preservation.
-
+This system employs a carefully engineered adaptation of the Plumbus Combobulator, which offers fault-tolerant characteristics and efficient data preservation.\par
+%
 At the core of the data storage mechanism is the utilization of punched tape, designed to withstand various environmental conditions.
 This robust material ensures the durability and integrity of the captured lightning data, even during adverse weather conditions such as rainfall.
-The waterproof nature of the tape safeguards the data from moisture, allowing for uninterrupted data collection.
-
+The waterproof nature of the tape safeguards the data from moisture, allowing for uninterrupted data collection.\par
+%
 The adapted Plumbus Combobulator employs a $\SI{0.47}{\micro\meter}$ needle, precisely marking the punched tape as the lightning data is processed.
 This needle-based mechanism creates a distinct pattern that represents the collected information.
-With each stroke, a tangible record of the lightning data is imprinted onto the punched tape.
-
+With each stroke, a tangible record of the lightning data is imprinted onto the punched tape.\par
+%
 The tape-based storage medium enables efficient and reliable data preservation.
 Each $\SI{100}{\milli\meter}$ segment of the punched tape corresponds to a substantial $\SI{1.2E6}{\byte}$ of information.
-This capacity ensures ample storage space for capturing an extensive volume of lightning data during experiments.
-
+This capacity ensures ample storage space for capturing an extensive volume of lightning data during experiments.\par
+%
 \section{Data Analysis}
-
+%
 \subsection{The Branzine levels}
-
+%
 According to the Plumbus Combobulator manufacturer's manual \citep{PlumbusManual}, high levels of Branzine can potentially lead to malfunctions in the Electroplumbus Nimbodetector.
-Therefore, a preliminary exploratory flight was conducted to investigate the relationship between altitude and Branzine levels.
+Therefore, a preliminary exploratory flight was conducted to investigate the relationship between altitude and Branzine levels.\par
+%
 During the flight, air samples were gathered at various altitudes to measure the concentration of Branzine, by using the Branzine detector\footnote{Digital Bz897U, available on $^{\circledR}$Airbone Laboratory Instrument Inc.}.
@@
 This differentiation aimed to explore any potential impact of precipitation on Branzine levels.
-
+%
 The  data was sent to the laboratory, and the results are bellow summarized:
-
+%
 \begin{table}[!h]
@@
 \vspace{-6mm}
+%
 Upon analyzing the data, it was observed that there is a increase in Branzine levels with increasing altitude.
@@
 These findings align with prior research \citep{Gagaia1923}, which suggests that Branzine levels typically exhibit a notable increase of over $5\%$ in some conditions such as winter seasons or above the Devil's Triangle ($32\%$).
-
+%
 \subsection{The radiation levels}
-
+%
 Despite the influence of Branzine on the detector, it has been determined that the Electroplumbus Nimbodetector is safe to use under the tested conditions.
-The Electroplumbus Nimbodetector was successfully installed on the 14-bis flying vehicle, and a series of tests were conducted at altitudes ranging from $\SI{100}{\meter}$ to $\SI{6000}{\meter}$.
-
+The Electroplumbus Nimbodetector was successfully installed on the 14-bis flying vehicle, and a series of tests were conducted at altitudes ranging from $\SI{100}{\meter}$ to $\SI{6000}{\meter}$.\par
+%
 The evaluation began by examining the performance of the Nimbus Detector under heavy rain conditions, comparing the recorded data to measurements obtained in a rainless environment above the clouds.
-A total of $\SI{12}{\meter}$ of data were collected and recorded on punched tape, with $\SI{30}{\centi\meter}$ obtained in the absence of rain and the remaining length obtained during rainfall.
-
+A total of $\SI{12}{\meter}$ of data were collected and recorded on punched tape, with $\SI{30}{\centi\meter}$ obtained in the absence of rain and the remaining length obtained during rainfall.\par
+%
 After the evaluation, the collected data in the form of punched tape was sent for analysis.
 The punched tape contained the recorded information obtained by the Nimbus Detector during the data collection.
-To process and analyze the data, the Monrobot XI computer was used, employing the Foobar Algorithm programmed in FORTRAN.
-The behavior of the sensor can be described by the Stefan-Boltzmann law, which relates the energy radiated by a black body to its temperature.
-
-According to the Stefan-Boltzmann law, the power radiated by a gray body is proportional to the fourth power of its absolute temperature $T$ and can be expressed as:
-
+To process and analyze the data, the Monrobot XI computer was used, employing the Foobar Algorithm programmed in FORTRAN (see listing \ref{lst:listing-f90}).
+The behavior of the sensor can be described by the Stefan-Boltzmann law, which relates the energy radiated by a black body to its temperature.\par
+%
+According to the Stefan-Boltzmann law, the power radiated by a gray body is proportional to the fourth power of its absolute temperature $T$ and can be expressed as:\par
+%
+\vspace{-10mm}
 \begin{equation}\label{StefanBoltzmannLaw}
@@
 The modified equation is as follows:
-
+%
+\vspace{-5mm}
 \begin{equation}
@@
 Also, $A$ is the surface sensor's area ($A=\SI{128.34}{\milli\meter^2}$).
-
+$T_v$ and $T_a$ are fuselage and air temperature, respectively.
+%
 \section{Results and Discussion}
-
+%
 The analysis of data collected by the Electroplumbus Nimbodetector reveals a significant correlation between the intensity of lightning strikes and the transfer of thermal radiation.
-Through a series of field experiments and measurements, we observed a consistent increase in the energy transferred by radiation during lightning events.
-
-\pgfplotstableread{multiple_functions.dat}{\table}
-
-\pgfplotsset{
-  legend style = {font = \large}, % Adjust the font size and style as needed
-  tick label style = {font = \Large}, % Adjust the font size as needed
-  every axis label = {font = \Large}, % Adjust the font size as needed
-}
-
+Through a series of field experiments and measurements, we observed a consistent increase in the energy transferred by radiation during lightning events.\par
+%
+\begin{figure}[!h]
+  \caption{Temperature gain as a function of Luminous intensity}
+  \vspace{-3mm} 
   \begin{center}
-  \begin{tikzpicture}[scale=0.7][H]
-\begin{axis}[
-    xmin = 0, xmax = 10,
-    ymin = 0, ymax = 1,
-    xtick distance = 1,
-    ytick distance = 0.25,
-    grid = both,
-    minor tick num = 1,
-    major grid style = {lightgray},
-    minor grid style = {lightgray!25},
-    width = \textwidth,
-    height = 0.6\textwidth,
-    legend cell align = {left},
-    legend pos = north west,
-    tick label style = {font = \scriptsize}, % Adjust the font size as needed
-    every axis label = {font = \small}, % Adjust the font size as needed
-    legend style = {font = \small} % Adjust the font size and style as needed
-]
-
-\addplot[blue, mark = *] table [x = {x}, y = {y1}] {\table};
-
-\addplot[red, only marks] table [x ={x}, y = {y2}] {\table};
-
-\addplot[teal, only marks, mark = x, mark size = 3pt] table [x = {x}, y = {y3}] {\table};
-
-\legend{
-    Plot with marks and line, 
-    Plot only with marks,
-    Plot with other type of marks
-}
-
-\end{axis}
-
-\end{tikzpicture}
+    \includegraphics[width=0.85\textwidth, trim={0 0 0 0},clip]{images/graph.png}
   \end{center}
-
-The chart presents the number of lightning strikes detected by the Nimbus Detector within different altitude ranges.
-As altitude increased, the number of recorded lightning strikes also exhibited an upward trend.\par
+  {\footnotesize Caption: Each set represents an altitude. The graph shows temperature rise as light intensity intensifies on heavy rain}
+  \label{fig:graph}
+\end{figure}
 %
-The chart presented in Figure 1 illustrates the relationship between the intensity of lightning strikes and the corresponding heat transfer rate by radiation.
+The chart presented in the figure \ref{fig:graph} illustrates the relationship between the intensity of lightning strikes and the corresponding heat transfer rate by radiation.
 As the intensity of the lightning strike increases, there is a clear upward trend in the energy transferred.
@@
 Some of these atoms vibrate with sufficient vigor that their vibrational energy matches the electronic energy (photons) absorbed from the lightning, effectively reaching resonance with the solar energy.
-As a result, these atoms undergo a quantum transition from being "electronically excited" to "vibrationally excited," causing the entire atom to move.
-The surrounding air perceives this excited vibration as "heat."\par
+As a result, these atoms undergo a quantum transition from being ``electronically excited" to ``vibrationally excited", causing the entire atom to move.
+The surrounding air perceives this excited vibration as ``heat."\par
 %
@@
 These findings contribute to the scientific understanding of lightning-induced thermal phenomena and lay the foundation for future research in this field.
-
+%
 \section*{Acknowledgements}
-
+%
 We gratefully acknowledge the Lupus Institute for their financial support, which has made this work possible.
 Also, we want to express our sincere appreciation to the open.ai for its invaluable assistance in the development of this fictional scientific paper.
-
+%
 \bibliography{references}
-
+%
 \theauthorcontributions
-
+%
 \howtocite
-
+%
 \section*{Appendix}
-\lstinputlisting[caption=Foobar program, label={lst:listing-f90}, language=Fortran]{foobar.f90}
-
+%
+\raggedleft\setstretch{1.0}\noindent
+\begin{minipage}[b]{\linewidth-6.5mm}
+  \lstinputlisting[caption=Foobar source code, label={lst:listing-f90}, language=Fortran]{foobar.f90}
+\end{minipage}
+%
 \end{document}

### 2023-06-02 paper.tex
new version

@@
 \documentclass[english]{cenarticle}
+% https://www.dropbox.com/scl/fo/mvds2vmlka4j33v69ip6r/h?dl=0&rlkey=osfeagghu2lh4qkr5ig9w0v47
+% https://www.dropbox.com/scl/fo/on0xgqzaeds3ys9b2sxxy/h?dl=0&rlkey=xvgm1v2arob7lzi7lvggmea81
 %
@@
 %
+%\addextraspaceoncoverpage{25mm}
 \coverpage
@@
   \begin{center}
-    \includegraphics[width=0.55\textwidth, trim={0 0 0 0},clip]{images/14-bis.jpeg}
+    \includegraphics[width=0.55\textwidth, trim={0 0 0 0},clip]{author_files/14-bis.jpeg}
   \end{center}
@@
     \begin{minipage}[t]{\x\linewidth}
-      \includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{images/nimbodetector.png}	
+      \includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{author_files/nimbodetector.png}	
       \captionsetup{justification=centering, font=footnotesize}
@@
     \begin{minipage}[t]{\x\linewidth}
-      \includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{images/sensor.png}	
+      \includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{author_files/sensor.png}	
       \captionsetup{justification=centering, font=footnotesize}
@@
 %
-\vspace{-5mm}
+\vspace{-1mm}
 \begin{equation}
@@
   \begin{center}
-    \includegraphics[width=0.85\textwidth, trim={0 0 0 0},clip]{images/graph.png}
+    \includegraphics[width=0.85\textwidth, trim={0 0 0 0},clip]{author_files/graph.png}
   \end{center}
@@
 %
-\theauthorcontributions
+\theauthorcontributions{authorshipAndContributions.tex}
 %

### 2023-06-02 script.sh

@@ -1,0 +1,65 @@
+#!/bin/bash
+
+authorFolder='author_files'
+authorFiles='https://uc4bc22013f2e02170fc540cb27a.dl.dropboxusercontent.com/zip_download_get/Bgk8QvqHfg6w99eXtgMeCJmsYNf1iOd0ImeP8glrC_0bNyIM0zsO70wjMwTAb4QvtOjWCBJOCwy40-wLSbgMDoIYlMxeiwjsVmHxVME3TW9LZA?_download_id=135192709297668253731150706657263684373260784521026549034371754102&_notify_domain=www.dropbox.com&dl=1'
+
+CENFolder='ciencia_e_natura_images'
+CENFiles='https://uc9ab9be8c1e8cd4d69d374244e2.dl.dropboxusercontent.com/zip_download_get/BgoKQfIIFM07Mp6FRe2SZJqwEaAcZKcRMS3dFFySpgnWauvyCXMeaQ5vfFBGi89CWE-uWmFCZ8zJu8tbfR3y4l7agbzb4pMAQJNnNtg2k-VQpw?_download_id=367960099149058364319372568591795028356855159465298846611692907312&_notify_domain=www.dropbox.com&dl=1'
+
+CENCoverPage='https://dl.dropboxusercontent.com/s/sa0nmq0xnrf6yeu/capa%202023.jpg?dl=0'
+
+if  ! [ -d "${authorFolder}" ]; then
+  mkdir "${authorFolder}"
+  curl -o author_files.zip "${authorFiles}"
+  unzip author_files.zip -d "${authorFolder}"
+  rm author_files.zip
+fi
+
+if ! [ -d "${CENFolder}" ]; then
+  mkdir ciencia_e_natura_images
+  curl -o journal_images.zip "${CENFiles}"
+  unzip journal_images.zip -d ciencia_e_natura_images
+  curl -o ciencia_e_natura_images/revista.jpg "${CENCoverPage}"
+  rm journal_images.zip
+fi
+
+if ! [ -f "foobar.f90" ]; then
+cat << EOF > foobar.f90
+  PROGRAM FOOBAR
+    IMPLICIT NONE
+  
+    INTEGER :: N, I
+    CHARACTER(LEN=9) :: MESSAGE
+  
+    WRITE(*, *) 'Enter a positive integer:'
+    READ(*, *) N
+  
+    DO I = 1, N
[…]

### 2023-06-03 script.sh
new version

@@ -1,26 +1,39 @@
 #!/bin/bash
 
 authorFolder='author_files'
-authorFiles='https://uc4bc22013f2e02170fc540cb27a.dl.dropboxusercontent.com/zip_download_get/Bgk8QvqHfg6w99eXtgMeCJmsYNf1iOd0ImeP8glrC_0bNyIM0zsO70wjMwTAb4QvtOjWCBJOCwy40-wLSbgMDoIYlMxeiwjsVmHxVME3TW9LZA?_download_id=135192709297668253731150706657263684373260784521026549034371754102&_notify_domain=www.dropbox.com&dl=1'
-
 CENFolder='ciencia_e_natura_images'
-CENFiles='https://uc9ab9be8c1e8cd4d69d374244e2.dl.dropboxusercontent.com/zip_download_get/BgoKQfIIFM07Mp6FRe2SZJqwEaAcZKcRMS3dFFySpgnWauvyCXMeaQ5vfFBGi89CWE-uWmFCZ8zJu8tbfR3y4l7agbzb4pMAQJNnNtg2k-VQpw?_download_id=367960099149058364319372568591795028356855159465298846611692907312&_notify_domain=www.dropbox.com&dl=1'
 
+#FROM MY PERSONAL REPO
+CENCenterLogo='https://dl.dropboxusercontent.com/s/ryy8ak0xoeqk76u/logo-ciencia-e-natura.jpg?dl=0'
+CENCreativeCommonsLogo='https://dl.dropboxusercontent.com/s/j33jzxl1cnllnsb/creativecommons.png?dl=0'
+
+AuthorImage14Bis='https://dl.dropboxusercontent.com/s/i7zkrwncj0lxkbs/14-bis.jpeg?dl=0'
+AuthorImageGraph='https://dl.dropboxusercontent.com/s/yqr1pqap1pgo7ob/graph.png?dl=0'
+AuthorImageNimbodetector='https://dl.dropboxusercontent.com/s/aoi3tyu7qhkxjjr/nimbodetector.png?dl=0'
+AuthorImageSensor='https://dl.dropboxusercontent.com/s/o4odbk9lqghke6j/sensor.png?dl=0'
+
+#FROM CENREPO
 CENCoverPage='https://dl.dropboxusercontent.com/s/sa0nmq0xnrf6yeu/capa%202023.jpg?dl=0'
+CENOpenAccessImage='https://dl.dropboxusercontent.com/s/61nilkod018iqng/OPEN%20ACCESS.png?dl=0'
[…]
